### 2010-09-06 annualreports/2010/balancesheet.tex
Initial import (annual report 2010)

\section{Balance Sheet}
31\superscript{st} March 2009

\begin{center}
\begin{tabular}{  l  r  r }
\toprule
                            & \multicolumn{2}{c}{2009} \\
\cmidrule(r){2-3}
                            & £     & £ \\
    \multicolumn{2}{c}{{\bf Fixed Assets}} &\\
    {\bf Tangible fixed assets}   &       & 1,054 \\ \cmidrule{2-3} \\
    \multicolumn{2}{c}{{\bf Current Assets}}&\\
    Cash at bank and in hand & 8,642 & \\
    Creditors: amounts falling due within one year & -1,343 & \\
    {\bf Net current assets}    &   & 7,299 \\ \cmidrule{2-3} \\
    {\bf Total assets less current liabilities} & & 8,354 \\ \cmidrule{2-3} \\
    \multicolumn{2}{c}{{\bf Capital and Reserves}}&\\
    Income and expenditure account     &   &   8,354 \\
\bottomrule
\end{tabular}

\end{center}

{\footnotesize For the financial period ended 31 March 2010 the
company was entitled to exemption from audit under section 477 of the
Companies Act 2006. No member of the company has deposited a
notice, pursuant to section 476, requiring an audit of these
financial statements under the requirements of the Companies Act
2006.

The directors acknowledge their responsibilities for ensuring that
the company keeps accounting records which comply with section 386
of the Act and for preparing financial statements which give a true
and fair view of the state of affairs of the company as at the end
of the financial period and of its profit or loss for the financial
period in accordance with the requirements of sections 394 and 395
and which otherwise comply with requirements of the Companies Act
2006 relating to accounts, so far as applicable to the company.

These financial statements have been prepared in accordance with
the special provisions relating to small companies within Part 15
of the Companies Act 2006 and with the Financial Reporting Standard
for Smaller Entities (effective April 2008).}

\vfill

Approved by the Board for issue on \\\\\\

Russell Garrett \\
{\bf Director} \\
Company Number: 06807563

\pagebreak

### 2010-09-06 annualreports/2010/directorsreport.tex
Initial import (annual report 2010)

\section{Directors' Report}

\subsection{Statement of Directors' Responsibilities}
The directors are responsible for preparing the Directors' Report and the financial statements in accordance with applicable law and regulations.

Company law requires the directors to prepare financial statements for each financial year. Under that law the directors have elected to prepare the financial statements in accordance with United Kingdom Generally Accepted Accounting Practice (United Kingdom Standards and applicable law). Under company law the directors must not approve the financial statements unless they are satisfied that they give a true and fair view of the state of affairs of the company and of the profit or loss of the company for that period. In preparing these financial statements, the directors are required to:

\begin{itemize}
    \item select suitable accounting policies and then apply them consistently;
    \item make judgements and accounting estimates that are reasonable and prudent;
    \item prepare the financial statements on the going concern basis unless it is inappropriate to presume that the company will continue in business.
\end{itemize}

The directors are responsible for keeping adequate accounting records that are sufficient to show and explain the company's transactions and disclose with reasonable accuracy at any time the financial position of the company and enable them to ensure that the financial statements comply with the Companies Act 2006. They are also responsible for safeguarding the assets of the company and hence for taking reasonable steps for the prevention and detection of fraud and other irregularities.

This report has been prepared in accordance with the special provisions relating to small companies within Part 15 of the Companies Act 2006.
\pagebreak

### 2010-09-06 annualreports/2010/notes.tex
Initial import (annual report 2010)

\section {Notes to the Financial Statements}
\begin{enumerate}
    \item {\bf Accounting policies}
    \begin{enumerate}
        \item {\bf Accounting convention} \\
                The financial statements are prepared under the 
            historical cost convention and in accordance with the Financial Reporting 
            Standard for Smaller Entities (effective April 2008).
        \item {\bf Compliance with accounting standards} \\
            The financial statements are prepared in accordance with applicable United
            Kingdom Accounting Standards (United Kingdom Generally Accepted Accounting
            Practice), which have been applied consistently throughout the period.
        \item {\bf Turnover} \\
            Turnover represents amounts receivable for services.
        \item {\bf Tangible fixed assets and depreciation} \\
            Tangible fixed assets are stated at cost less depreciation. Depreciation is
            provided at rates calculated to write off the cost less estimated residual
            value of each asset over its expected useful life, as follows: \\
            \begin{tabular}{  l  p{6.5cm} }
                \toprule
                Fixtures \& Fittings & Over 3 years at 33\% per annum on a straight line basis \\
                Plant \& Machinery & Over 3 years at 33\% per annum on a straight line basis \\
                \bottomrule
            \end{tabular}
    \end{enumerate}
\end{enumerate}

### 2010-10-02 annualreports/2010/directorsreport.tex
Fixes. This is the version submitted to Companies House

@@
 \section{Directors' Report}
+
+\subsection{Corporation Tax}
+As all members of the London Hackspace are also members of the company, we believe
+that we are trading under the mutual trading/membership associations exemption from corporation tax.
+
+As such, we believe that the Hackspace Foundation is not liable for any significant amount of
+corporation tax in this financial year.
 
@@
 This report has been prepared in accordance with the special provisions relating to small companies within Part 15 of the Companies Act 2006.
-\pagebreak
+
+Approved by the Board for issue on 6\superscript{th} September 2010.
+\vspace{48pt}
+
+Russell Garrett \\
+{\bf Director} \\
+Company Number: 06807563

### 2010-10-02 annualreports/2010/notes.tex
Fixes. This is the version submitted to Companies House

@@
             provided at rates calculated to write off the cost less estimated residual
-            value of each asset over its expected useful life, as follows: \\
+            value of each asset over its expected useful life, as follows: \\[6pt]
             \begin{tabular}{  l  p{6.5cm} }

### 2011-05-15 annualreports/2011/balancesheet.tex
Draft of the 2011 report.

--- 2010-09-06 annualreports/2010/balancesheet.tex
@@
 \section{Balance Sheet}
-31\superscript{st} March 2009
+31\superscript{st} March 2011
 
 \begin{center}
-\begin{tabular}{  l  r  r }
+\begin{tabular}{  l  r  r r r}
 \toprule
-                            & \multicolumn{2}{c}{2009} \\
-\cmidrule(r){2-3}
-                            & £     & £ \\
-    \multicolumn{2}{c}{{\bf Fixed Assets}} &\\
-    {\bf Tangible fixed assets}   &       & 1,054 \\ \cmidrule{2-3} \\
-    \multicolumn{2}{c}{{\bf Current Assets}}&\\
-    Cash at bank and in hand & 8,642 & \\
-    Creditors: amounts falling due within one year & -1,343 & \\
-    {\bf Net current assets}    &   & 7,299 \\ \cmidrule{2-3} \\
-    {\bf Total assets less current liabilities} & & 8,354 \\ \cmidrule{2-3} \\
-    \multicolumn{2}{c}{{\bf Capital and Reserves}}&\\
-    Income and expenditure account     &   &   8,354 \\
+                            & \multicolumn{2}{c}{2011} &  \multicolumn{2}{c}{2010} \\
+\cmidrule(r){2-3} \cmidrule(r){4-5}
+                                                & £     & £     & £     & £     \\
+{\bf Fixed Assets}                              &       &       &       &       \\
+{\bf Tangible fixed assets}                     &       & 5,337 &       & 1,054 \\
+\cmidrule(r){2-3} \cmidrule(r){4-5} \\
+{\bf Current Assets}                            &       &       &       &       \\
+Rental Deposit                                  & 7,696 &       &       &       \\
+Cash at bank and in hand                        & 7,568 &       & 8,642 &       \\
+Creditors: amounts falling due within one year  & -1,979 &      & -1,343&      \\
+{\bf Net current assets}                        &       & 13,285&       & 7,299 \\
+\cmidrule(r){2-3} \cmidrule(r){4-5} \\
+{\bf Total assets less current liabilities}     &       & 18,622&       & 8,354 \\
+\cmidrule(r){2-3} \cmidrule(r){4-5}  \\
+{\bf Capital and Reserves}&\\
+Income and expenditure account                  &       & 10,269&       & 8,354 \\
 \bottomrule
@@
 
-Approved by the Board for issue on \\\\\\
+Approved by the Board for issue on <date>
+\vspace{48pt}
 
@@
 Company Number: 06807563
-
-\pagebreak

### 2011-05-15 annualreports/2011/directorsreport.tex
Draft of the 2011 report.

\section{Directors' Report}

\subsection{Objects of the Company}

The stated Objects of the Hackspace Foundation are:

\begin{itemize}
    \item To promote and support science, engineering, and art.
\end{itemize}

The main activity of the company is providing permanent community workspace facilities in the London area (the London Hackspace).
We aim to provide a comfortable place where people can learn new skills, socialise, and gain access to tools they would not otherwise have access to.

\subsection{Organisational Structure}\label{ref_structure}

The Hackspace Foundation is a Company Limited by Guarantee operating as a membership association.
The company has a Board of up to eight Directors who are elected by the membership and serve for a three-year term,
although this is mainly a symbolic role with most decisions made by membership consensus.

As the Foundation has grown since its formation in February 2009, it has historically not been possible
to reliably determine if it is eligible for charitable status. Combined with the administrative overhead of doing so,
this has so far prevented the Hackspace Foundation from becoming a registered charity.

Since the company is becoming more mature, it is becoming more clear that it is likely to be eligible for charitable status,
and we anticipate looking into applying within the next year.

\subsection{Facilities}

At the beginning of the 2010/2011 year, the London Hackspace was based in an 800 sq ft, unheated space in Barnsbury.
In July 2010 we moved to a 1300 sq ft space in Cremer Street, E2, and on January 1\(^{st}\) 2011 the space was expanded into
the adjacent unit to increase our space to 2600 sq ft.

Currently our space comprises desk space across two separate rooms, sofas, a kitchen, and a sizeable workshop with woodworking,
metalworking and other fabrication facilities.

Recent equipment purchases include a laser cutter for cutting and etching wood and plastic, and large lathe/mill for metalworking.
All this equipment is available for members to use for free or with a small contribution to equipment running costs.

\subsection{Membership}

The Hackspace Foundation is a membership association, and membership is open to everyone.
Members receive 24-hour access to the space, storage space, and voting rights in return for a membership subscription.

The minimum membership subscription is £5 per month, and members are encouraged to pay what they consider their
membership to be worth.

Membership subscriptions are the primary source of income for the Hackspace Foundation, and in 2010/11 our
membership rapidly grew by 600\% from 41 to 252 people.

\subsection{Services for Non-Members}

Although we encourage anyone who finds the London Hackspace useful to become a member, we don't limit our services to members.
Non-members can use our facilities under the supervision of a member, and we run events (both free and paid) which are open to non-members.

There are many individual events organised by members on a regular basis, which are usually free and open to the public. Regular events include:

\begin{itemize}
    \item Weekly Meetups - our weekly public social events.
    \item DIY Bio - workshops and lectures on biology.
    \item Young Hackspace - free events for children aged between 6 and 10.
\end{itemize}

We also allow other like-minded non-profit groups to hire out sections of our space at cost - generally much cheaper than other similar venues.

\subsection{Public Benefit}

The London Hackspace is not currently a registered charity (see the Organisational Structure section on page \pageref{ref_structure} for more details),
which would require it to publish details of the public benefit it delivers. Nonetheless, the Directors feel it is appropriate to do so.

We believe the London Hackspace delivers charitable benefits under two of the headings allowed by the Charities Act 2006:
firstly and primarily through the advancement of the arts, culture, heritage or science, and secondly through the advancement of education.

As entry to the London Hackspace is free of charge for non-members, and the minimum membership is a modest fee, we
believe there are no unreasonable restrictions on access to the benefits which are therefore available to the public in accordance with the
definition of the Act.

\subsection{Reserves Policy}

The Hackspace Foundation aims to keep three months worth of monthly running costs as a reserve. This currently amounts to £12,486.

Due to the significant membership growth of the London Hackspace during 2010/11, it was decided to spend some of the reserve on expanding the space.
The majority of this was spent on lease deposits. At the end of the financial year, our balance was £7,568.

\subsection{Statement of Directors' Responsibilities}
The directors are responsible for preparing the Directors' Report and the financial statements in accordance with applicable law and regulations.

Company law requires the directors to prepare financial statements for each financial year. Under that law the directors have elected to prepare the financial statements in accordance with United Kingdom Generally Accepted Accounting Practice (United Kingdom Standards and applicable law). Under company law the directors must not approve the financial statements unless they are satisfied that they give a true and fair view of the state of affairs of the company and of the profit or loss of the company for that period. In preparing these financial statements, the directors are required to:

\begin{itemize}
    \item select suitable accounting policies and then apply them consistently;
    \item make judgements and accounting estimates that are reasonable and prudent;
    \item prepare the financial statements on the going concern basis unless it is inappropriate to presume that the company will continue in business.
\end{itemize}

The directors are responsible for keeping adequate accounting records that are sufficient to show and explain the company's transactions and disclose with reasonable accuracy at any time the financial position of the company and enable them to ensure that the financial statements comply with the Companies Act 2006. They are also responsible for safeguarding the assets of the company and hence for taking reasonable steps for the prevention and detection of fraud and other irregularities.

This report has been prepared in accordance with the special provisions relating to small companies within Part 15 of the Companies Act 2006.

Approved by the Board for issue on <date>
\vspace{48pt}

Russell Garrett \\
{\bf Director} \\
Company Number: 06807563

### 2011-06-01 constitution/articles-body.tex
Switch to formatting using tex

\title{Articles of Association of London Hackspace Ltd.}
\begin{enumerate}
\item
  The company's name is London Hackspace Ltd. (and in this document
  it is called the ``charity'').

\section{Interpretation}

\item
  In the articles:
  \begin{itemize}
  \item
    ``address'' means a postal address or, for the purposes of
    electronic communication, a fax number, an e-mail or postal address
    or a telephone number for receiving text messages in each case
    registered with the charity;
  \item
    ``the articles'' means the charity's articles of association;
  \item
    ``the charity'' means the company intended to be regulated by the
    articles;
  \item
    ``clear days'' in relation to the period of a notice means a period
    excluding:
    \begin{itemize}
    \item
      the day when the notice is given or deemed to be given; and
    \item
      the day for which it is given or on which it is to take effect;
    \end{itemize}
  \item
    ``the Commission'' means the Charity Commission for England and
    Wales;
  \item
    ``Companies Acts'' means the Companies Acts (as defined in section
    2 of the Companies Act 2006) insofar as they apply to the charity;
  \item
    ``the directors'' means the directors of the charity. The directors
    are charity trustees as defined by section 97 of the Charities Act
    1993;
  \item
    ``document'' includes, unless otherwise specified, any document
    sent or supplied in electronic form;
  \item
    ``electronic form'' has the meaning given in section 1168 of
    theCompanies Act 2006;
  \item
    ``the memorandum'' means the charity's memorandum of association;
  \item
    ``officers'' includes the directors and the secretary (if any);
  \item
    ``the seal'' means the common seal of the charity if it has one;
  \item
    ``secretary'' means any person appointed to perform the duties of
    the secretary of the charity;
  \item
    ``the United Kingdom'' means Great Britain and Northern Ireland;
    and
  \item
    words importing one gender shall include all genders, and the
    singular includes the plural and vice versa.
  \end{itemize}
  Unless the context otherwise requires words or expressions
  contained in the articles have the same meaning as in the Companies
  Acts but excluding any statutory modification not in force when
  this constitution becomes binding on the charity.

  Apart from the exception mentioned in the previous paragraph a
  reference to an Act of Parliament includes any statutory
  modification or re-enactment of it for the time being in force.

\section{Liability of Members}

\item
  The liability of the members is limited to a sum not exceeding £1,
  being the amount that each member undertakes to contribute to the
  assets of the charity in the event of its being wound up while he,
  she or it is a member or within one year after he, she or it ceases
  to be a member, for:
  \begin{enumerate}
  \item
    payment of the charity's debts and liabilities incurred before he,
    she or it ceases to be a member;
  \item
    payment of the costs, charges and expenses of winding up; and
  \item
    adjustment of the rights of the contributories among themselves.
  \end{enumerate}

\section{Objects}

\item
  The charity's objects (``Objects'') are specifically restricted to
  the following:
  \begin{enumerate}
  \item
    to promote and encourage technical, scientific, and artistic skills through social collaboration and education; and
  \item
    to provide and maintain shared community workspace and equipment for the use of the residents of London.
  \end{enumerate}

\section{Powers}

\item
  The charity has power to do anything which is calculated to further
  its Objects or is conducive or incidental to doing so. In
  particular, the charity has power:
  \begin{enumerate}
  \item
    to raise funds. In doing so, the charity must not undertake any
    taxable permanent trading activity and must comply with any
    relevant statutory regulations;
  \item
    to buy, take on lease or in exchange, hire or otherwise acquire any
    property and to maintain and equip it for use;
  \item
    to sell, lease or otherwise dispose of all or any part of the
    property belonging to the charity. In exercising this power, the
    charity must comply as appropriate with sections 36 and 37 of the
    Charities Act 1993, as amended by the Charities Act 2006;
  \item
    to borrow money and to charge the whole or any part of the property
    belonging to the charity as security for repayment of the money
    borrowed or as security for a grant or the discharge of an
    obligation. The charity must comply as appropriate with sections 38
    and 39 of the Charities Act 1993, as amended by the Charities Act
    2006, if it wishes to mortgage land;
  \item
    to co-operate with other charities, voluntary bodies and statutory
    authorities and to exchange information and advice with them;
  \item
    to establish or support any charitable trusts, associations or
    institutions formed for any of the charitable purposes included in
    the Objects;
  \item
    to acquire, merge with or to enter into any partnership or joint
    venture arrangement with any other charity;
  \item
    to set aside income as a reserve against future expenditure but
    only in accordance with a written policy about reserves;
  \item
    to employ and remunerate such staff as are necessary for carrying
    out the work of the charity. The charity may employ or remunerate a
    director only to the extent it is permitted to do so by article \ref{cls:income-property}
    and provided it complies with the conditions in that article;
  \item
    to:
    \begin{enumerate}
    \item
      deposit or invest funds;
    \item
      employ a professional fund-manager; and
    \item
      arrange for the investments or other property of the charity to be
      held in the name of a nominee; in the same manner and subject to
      the same conditions as the trustees of a trust are permitted to do
      by the Trustee Act 2000;
    \end{enumerate}
  \item
    to provide indemnity insurance for the directors in accordance
    with, and subject to the conditions in, section 73F of the
    Charities Act 1993;
  \item
    to pay out of the funds of the charity the costs of forming and
    registering the charity both as a company and as a charity;
  \end{enumerate}

\section{Application of Income and Property}

\item
  \label{cls:income-property}
  \begin{enumerate}
  \item
    The income and property of the charity shall be applied solely
    towards the promotion of the Objects.
  \item
    \label{scls:director-reimburse}
    \begin{enumerate}
    \item
      A director is entitled to be reimbursed from the property of the
      charity or may pay out of such property reasonable expenses
      properly incurred by him or her when acting on behalf of the
      charity.
    \item
      A director may benefit from trustee indemnity insurance cover
      purchased at the charity's expense in accordance with, and subject
      to the conditions in, section 73F of the Charities Act 1993.
    \item
      A director may receive an indemnity from the charity in the
      circumstances specified in article \ref{cls:directors-indemnity}.
    \end{enumerate}
  \item
    None of the income or property of the charity may be paid or
    transferred directly or indirectly by way of dividend bonus or
    otherwise by way of profit to any member of the charity. This does
    not prevent a member who is not also a director receiving:
    \begin{enumerate}
    \item
      a benefit from the charity in the capacity of a beneficiary of the
      charity;
    \item
      reasonable and proper remuneration for any goods or services
      supplied to the charity.
    \end{enumerate}
  \item
    \label{scls:directors-remuneration} No director or connected person
    may:
    \begin{enumerate}
    \item
      buy any goods or services from the charity on terms preferential to
      those applicable to members of the public;
    \item
      sell goods, services, or any interest in land to the charity;
    \item
      be employed by, or receive any remuneration from, the charity;
    \item
      receive any other financial benefit from the charity; unless:
      \begin{enumerate}
      \item
        the payment is permitted by article \ref{scls:directors-scope}; or
      \item
        the directors obtain the prior written approval of the Commission
        and fully comply with any procedures it prescribes. In this article
        a `financial benefit' means a benefit, direct or indirect, which is
        either money or has a monetary value.
      \end{enumerate}
    \end{enumerate}
  \item
    \label{scls:directors-scope}
    \begin{enumerate}
    \item
      A director or connected person may receive a benefit from the
      charity as a beneficiary provided it is available generally to the
      beneficiaries of the charity.
    \item
      A director or connected person may enter into a contract for the
      supply of services, or of goods that are supplied in connection
      with the provision of services, to the charity where that is
      permitted in accordance with, and subject to the conditions in
      section 73A to 73C of the Charities Act 1993.
    \item
      Subject to article \ref{scls:supply-goods} a director or connected
      person may provide the charity with goods that are not supplied in
      connection with services provided to the charity by the director or
      connected person. \label{art:directors-goods}
    \item
      A director or connected person may receive interest on money lent
      to the charity at a reasonable and proper rate which must be 2\%
      (or more) per annum below the base rate of a clearing bank to be
      selected by the directors.
    \item
      A director or connected person may receive rent for premises let by
      the director or connected person to the charity if the amount of
      the rent and the other terms of the lease are reasonable and proper
      and provided that the director concerned shall withdraw from any
      meeting at which such a proposal or the rent or other terms of the
      lease are under discussion.
    \item
      The directors may arrange for the purchase, out of the funds of the
      charity, of insurance designed to indemnify the directors in
      accordance with the terms of, and subject to the conditions in,
      section 73F of the Charities Act 1993.
    \end{enumerate}
  \item \label{goods}
    \label{scls:supply-goods} The charity and its directors may only
    rely upon the authority provided by article
    \ref{art:directors-goods} if each of the following conditions is
    satisfied:
    \begin{enumerate}
    \item
      The amount or maximum amount of the payment for the goods is set
      out in an agreement in writing between:
      \begin{enumerate}
      \item
        the charity or its directors (as the case may be); and
      \item
        the director or connected person supplying the goods
        (``the supplier'') under which the supplier is to supply the goods
        in question to or on behalf of the charity.
      \end{enumerate}
    \item
      The amount or maximum amount of the payment for the goods does not
      exceed what is reasonable in the circumstances for the supply of
      the goods in question.
    \item
      The other directors are satisfied that it is in the best interests
      of the charity to contract with the supplier rather than with
      someone who is not a director or connected person. In reaching that
      decision the directors must balance the advantage of contracting
      with a director or connected person against the disadvantages of
      doing so.
    \item
      The supplier is absent from the part of any meeting at which there
      is discussion of the proposal to enter into a contract or
      arrangement with him or her or it with regard to the supply of
      goods to the charity.
    \item
      The supplier does not vote on any such matter and is not to be
      counted when calculating whether a quorum of directors is present
      at the meeting.
    \item
      The reason for their decision is recorded by the directors in the
      minute book.
    \item
      A majority of the directors then in office are not in receipt of
      remuneration or payments authorised by article
      \ref{scls:directors-remuneration}.
    \end{enumerate}
  \item \label{def-charity}
    In sub-clauses \ref{scls:director-reimburse} to \ref{goods}, ``charity'' shall include
    any company in which the charity:
    \begin{itemize}
    \item
      holds more than 50\% of the shares; or
    \item
      controls more than 50\% of the voting rights attached to the
      shares; or
    \item
      has the right to appoint one or more directors to the board of the
      company;
    \end{itemize}
  \item \label{def-connected}
    In sub-clauses \ref{scls:directors-remuneration} to \ref{goods}, \ref{conflict-interest-loyalty},
    and \ref{directors-validity-void} ``connected person'' means:
    \begin{enumerate}
    \item
      \label{art:connected-child} a child, parent, grandchild,
      grandparent, brother or sister of the director;
    \item
      \label{art:connected-spouse} the spouse or civil partner of the
      director or of any person falling within paragraph (i) above;
    \item
      \label{art:connected-business} a person carrying on business in
      partnership with the director or with any person falling within
      paragraph (i) or (ii)above;
    \item
      an institution which is controlled –
      \begin{enumerate}
      \item
        by the director or any connected person falling within paragraph (i) to (iii) above; or
      \item
        by two or more persons falling within sub-paragraph (A), when taken
        together
      \end{enumerate}
    \item
      a body corporate in which –
      \begin{enumerate}
        \item
            the director or any connected person falling within paragraphs (i) to (iii) has a substantial interest; or
        \item
            two or more persons falling within sub-paragraph (A) who, when
            taken together, have a substantial interest.
      \end{enumerate}
    \end{enumerate}
  \item
    For the purposes of interpreting the terms used in sub-clauses \ref{def-charity}
    and \ref{def-connected}, paragraphs 2 to 4 of Schedule 5 to the Charities Act 1993
    apply.
  \end{enumerate}

\section{Members}

\item
  \label{cls:subscribers}
  \begin{enumerate}
  \item
    The subscribers to the memorandum are the first members of the
    charity.
  \item
    Membership is open to other individuals or organisations who:
    \begin{enumerate}
    \item
      apply to the charity in the form required by the directors; and
    \item
      are approved by the directors.
    \end{enumerate}
  \item

    \begin{enumerate}
    \item
      The directors may only refuse an application for membership if,
      acting reasonably and properly, they consider it to be in the best
      interests of the charity to refuse the application.
    \item
      The directors must inform the applicant in writing of the reasons
      for the refusal within twenty-one days of the decision.
    \item
      The directors must consider any written representations the
      applicant may make about the decision. The directors' decision
      following any written representations must be notified to the
      applicant in writing but shall be final.
    \end{enumerate}
  \item
    Membership is not transferable.
  \item
    The directors must keep a register of names and addresses of the
    members.
  \end{enumerate}

\section{Classes of Membership}

\item
  \label{cls:members}
  \begin{enumerate}
  \item
    The directors may establish classes of membership with different
    rights and obligations and shall record the rights and obligations
    in the register of members.
  \item
    The directors may not directly or indirectly alter the rights or
    obligations attached to a class of membership.
  \item
    The rights attached to a class of membership may only be varied if:
    \begin{enumerate}
    \item
      three-quarters of the members of that class consent in writing to
      the variation; or
    \item
      a special resolution is passed at a separate general meeting of the
      members of that class agreeing to the variation.
    \end{enumerate}
  \item
    The provisions in the articles about general meetings shall apply
    to any meeting relating to the variation of the rights of any class
    of members.
  \end{enumerate}

\section{Termination of Membership}

\item
  Membership is terminated if:
  \begin{enumerate}
  \item
    the member dies or, if it is an organisation, ceases to exist;
  \item
    the member resigns by written notice to the charity unless, after
    the resignation, there would be less than two members;
  \item
    any sum due from the member to the charity is not paid in full
    within six months of it falling due;
  \item
    the member is removed from membership by a resolution of the
    directors that it is in the best interests of the charity that his
    or her or its membership is terminated. A resolution to remove a
    member from membership may only be passed if:
    \begin{enumerate}
    \item
      the member has been given at least twenty-one days' notice in
      writing of the meeting of the directors at which the resolution
      will be proposed and the reasons why it is to be proposed;
    \item
      the member or, at the option of the member, the member's
      representative (who need not be a member of the charity) has been
      allowed to make representations to the meeting.
    \end{enumerate}
  \end{enumerate}

\section{General Meetings}

\item
  \begin{enumerate}
  \item
    The charity must hold its first annual general meeting within
    eighteen months after the date of its incorporation.
  \item
    An annual general meeting must be held in each subsequent year and
    not more than fifteen months may elapse between successive annual
    general meetings.
  \end{enumerate}
\item
  The directors may call a general meeting at any time.

\section{Notice of General Meetings}

\item
  \begin{enumerate}
  \item
    The minimum periods of notice required to hold a general meeting of
    the charity are:
    \begin{enumerate}
    \item
      twenty-one clear days for an annual general meeting or a general
      meeting called for the passing of a special resolution;
    \item
      fourteen clear days for all other general meetings.
    \end{enumerate}
  \item
    A general meeting may be called by shorter notice if it is so
    agreed by a majority in number of members having a right to attend
    and vote at the meeting, being a majority who together hold not
    less than 90 percent of the total voting rights.
  \item
    The notice must specify the date time and place of the meeting and
    the general nature of the business to be transacted. If the meeting
    is to be an annual general meeting, the notice must say so. The
    notice must also contain a statement setting out the right of
    members to appoint a proxy under section 324 of the Companies Act
    2006 and article \ref{proxies}.
  \item
    The notice must be given to all the members and to the directors
    and auditors.
  \end{enumerate}

\item
  The proceedings at a meeting shall not be invalidated because a
  person who was entitled to receive notice of the meeting did not
  receive it because of an accidental omission by the charity.

\section{Proceedings at General Meetings}

\item
  \begin{enumerate}
  \item
    No business shall be transacted at any general meeting unless a
    quorum is present.
  \item
    A quorum is:
    \begin{enumerate}
    \item x members present in person or by proxy and entitled to vote upon
      the business to be conducted at the meeting; or
    \item
      one tenth of the total membership at the time
    \end{enumerate}
  \item
    The authorised representative of a member organisation shall be
    counted in the quorum.
  \end{enumerate}

\item
  \begin{enumerate}
  \item
    If :
    \begin{enumerate}
    \item
      a quorum is not present within half an hour from the time appointed
      for the meeting; or
    \item
      during a meeting a quorum ceases to be present; the meeting shall
      be adjourned to such time and place as the directors shall
      determine.
    \end{enumerate}
  \item
    The directors must reconvene the meeting and must give at least
    seven clear days' notice of the reconvened meeting stating the
    date, time and place of the meeting.
  \item
    If no quorum is present at the reconvened meeting within fifteen
    minutes of the time specified for the start of the meeting the
    members present in person or by proxy at that time shall constitute
    the quorum for that meeting.
  \end{enumerate}
\item

  \begin{enumerate}
  \item
    General meetings shall be chaired by the person who has been
    appointed to chair meetings of the directors.
  \item
    If there is no such person or he or she is not present within
    fifteen minutes of the time appointed for the meeting a director
    nominated by the directors shall chair the meeting.
  \item
    If there is only one director present and willing to act, he or she
    shall chair the meeting.
  \item
    If no director is present and willing to chair the meeting within
    fifteen minutes after the time appointed for holding it, the
    members present in person or by proxy and entitled to vote must
    choose one of their number to chair the meeting.
  \end{enumerate}
\item

  \begin{enumerate}
  \item
    The members present in person or by proxy at a meeting may resolve
    by ordinary resolution that the meeting shall be adjourned.
  \item
    The person who is chairing the meeting must decide the date, time
    and place at which the meeting is to be reconvened unless those
    details are specified in the resolution.
  \item
    No business shall be conducted at a reconvened meeting unless it
    could properly have been conducted at the meeting had the
    adjournment not taken place.
  \item
    If a meeting is adjourned by a resolution of the members for more
    than seven days, at least seven clear days' notice shall be given
    of the reconvened meeting stating the date, time and place of the
    meeting.
  \end{enumerate}
\item

  \begin{enumerate}
  \item
    Any vote at a meeting shall be decided by a show of hands unless
    before, or on the declaration of the result of, the show of hands a
    poll is demanded:
    \begin{enumerate}
    \item
      by the person chairing the meeting; or
    \item
      by at least two members present in person or by proxy and having
      the right to vote at the meeting; or
    \item
      by a member or members present in person or by proxy representing
      not less than one-tenth of the total voting rights of all the
      members having the right to vote at the meeting.
    \end{enumerate}
  \item

    \begin{enumerate}
    \item
      The declaration by the person who is chairing the meeting of the
      result of a vote shall be conclusive unless a poll is demanded.
    \item
      The result of the vote must be recorded in the minutes of the
      charity but the number or proportion of votes cast need not be
      recorded.
    \end{enumerate}
  \item

    \begin{enumerate}
    \item
      A demand for a poll may be withdrawn, before the poll is taken, but
      only with the consent of the person who is chairing the meeting.
    \item
      If the demand for a poll is withdrawn the demand shall not
      invalidate the result of a show of hands declared before the demand
      was made.
    \end{enumerate}
  \item

    \begin{enumerate}
    \item
      A poll must be taken as the person who is chairing the meeting
      directs, who may appoint scrutineers (who need not be members) and
      who may fix a time and place for declaring the results of the poll.
    \item
      The result of the poll shall be deemed to be the resolution of the
      meeting at which the poll is demanded.
    \end{enumerate}
  \item

    \begin{enumerate}
    \item
      A poll demanded on the election of a person to chair a meeting or
      on a question of adjournment must be taken immediately.
    \item
      A poll demanded on any other question must be taken either
      immediately or at such time and place as the person who is chairing
      the meeting directs.
    \item
      The poll must be taken within thirty days after it has been
      demanded.
    \item
      If the poll is not taken immediately at least seven clear days'
      notice shall be given specifying the time and place at which the
      poll is to be taken.
    \item
      If a poll is demanded the meeting may continue to deal with any
      other business that may be conducted at the meeting.
    \end{enumerate}
  \end{enumerate}

\section{Content of Proxy Notices}

\item \label{proxies}
  \begin{enumerate}
  \item
    Proxies may only validly be appointed by a notice in writing (a
    ``proxy notice'') which -
    \begin{enumerate}
    \item
      states the name and address of the member appointing the proxy;
    \item
      identifies the person appointed to be that member's proxy and the
      general meeting in relation to which that person is appointed;
    \item
      is signed by or on behalf of the member appointing the proxy, or is
      authenticated in such manner as the directors may determine; and
    \item
      is delivered to the charity in accordance with the articles and any
      instructions contained in the notice of the general meeting to
      which they relate.
    \end{enumerate}
  \item
    The charity may require proxy notices to be delivered in a
    particular form, and may specify different forms for different
    purposes.
  \item
    Proxy notices may specify how the proxy appointed under them is to
    vote (or that the proxy is to abstain from voting) on one or more
    resolutions.
  \item
    Unless a proxy notice indicates otherwise, it must be treated as -
    \begin{enumerate}
    \item
      allowing the person appointed under it as a proxy discretion as to
      how to vote on any ancillary or procedural resolutions put to the
      meeting; and
    \item
      appointing that person as a proxy in relation to any adjournment of
      the general meeting to which it relates as well as the meeting
      itself.
    \end{enumerate}
  \end{enumerate}

\section{Delivery of Proxy Notices}

\item
    \begin{enumerate}
        \item
        A person who is entitled to attend, speak or vote
        (either on a show of hands or on a poll) at a general meeting
        remains so entitled in respect of that meeting or any adjournment
        of it, even though a valid proxy notice has been delivered to the
        charity by or on behalf of that person.
        \item
        An appointment under a
        proxy notice may be revoked by delivering to the charity a notice
        in writing given by or on behalf of the person by whom or on whose
        behalf the proxy notice was given. 
        \item
        A notice revoking a proxy
        appointment only takes effect if it is delivered before the start
        of the meeting or adjourned meeting to which it relates 
        \item
        If a
        proxy notice is not executed by the person appointing the proxy, it
        must be accompanied by written evidence of the authority of the
        person who executed it to execute it on the appointor's behalf.
    \end{enumerate}

\section{Written Resolutions}

\item
  \begin{enumerate}
  \item
    A resolution in writing agreed by a simple majority (or in the case
    of a special resolution by a majority of not less than 75\%) of the
    members who would have been entitled to vote upon it had it been
    proposed at a general meeting shall be effective provided that:
    \begin{enumerate}
    \item
      a copy of the proposed resolution has been sent to every eligible
      member;
    \item
      a simple majority (or in the case of a special resolution a
      majority of not less than 75\%) of members has signified its
      agreement to the resolution; and
    \item
      it is contained in an authenticated document which has been
      received at the registered office within the period of 28 days
      beginning with the circulation date.
    \end{enumerate}
  \item
    A resolution in writing may comprise several copies to which one or
    more members have signified their agreement.
  \item
    In the case of a member that is an organisation, its authorised
    representative may signify its agreement.
  \end{enumerate}
\item
  Subject to article \ref{cls:members}, every member, whether an individual or an
  organisation, shall have one vote.

\section{Votes of Members}

\item
  Any objection to the qualification of any voter must be raised at
  the meeting at which the vote is tendered and the decision of the
  person who is chairing the meeting shall be final.
\item
  \begin{enumerate}
  \item
    Any organisation that is a member of the charity may nominate any
    person to act as its representative at any meeting of the charity.
  \item
    The organisation must give written notice to the charity of the
    name of its representative. The representative shall not be
    entitled to represent the organisation at any meeting unless the
    notice has been received by the charity. The representative may
    continue to represent the organisation until written notice to the
    contrary is received by the charity.
  \item
    Any notice given to the charity will be conclusive evidence that
    the representative is entitled to represent the organisation or
    that his or her authority has been revoked. The charity shall not
    be required to consider whether the representative has been
    properly appointed by the organisation.
  \end{enumerate}

\section{Directors}

\item
  \begin{enumerate}
  \item
    A director must be a natural person aged 16 years or older.
  \item
    No one may be appointed a director if he or she would be
    disqualified from acting under the provisions of article \ref{director-cease}.
  \end{enumerate}
\item
  The number of directors shall be not less than three but (unless
  otherwise determined by ordinary resolution) shall not be subject
  to any maximum.

\item
  The first directors shall be those persons notified to Companies
  House as the first directors of the charity.

\item
  A director may not appoint an alternate director or anyone to act
  on his or her behalf at meetings of the directors.

\section{Powers of Directors}

\item
  \begin{enumerate}
  \item
    The directors shall manage the business of the charity and may
    exercise all the powers of the charity unless they are subject to
    any restrictions imposed by the Companies Acts, the articles or any
    special resolution.
  \item
    No alteration of the articles or any special resolution shall have
    retrospective effect to invalidate any prior act of the directors.
  \item
    Any meeting of directors at which a quorum is present at the time
    the relevant decision is made may exercise all the powers
    exercisable by the directors.
  \end{enumerate}

\section{Retirement of Directors}

\item
    At the first annual general meeting all the directors must retire from
    office unless by the close of the meeting the members have failed to
    elect sufficient directors to hold a quorate meeting of the directors. At
    each subsequent annual general meeting one-third of the directors or, if
    their number is not three or a multiple of three, the number nearest to
    one-third, must retire from office. If there is only one director he or she
    must retire.

\item
  \begin{enumerate}
  \item
    The directors to retire by rotation shall be those who have been
    longest in office since their last appointment. If any directors
    became or were appointed directors on the same day those to retire
    shall (unless they otherwise agree among themselves) be determined
    by lot.
  \item
    If a director is required to retire at an annual general meeting by
    a provision of the articles the retirement shall take effect upon
    the conclusion of the meeting.
  \end{enumerate}

\section{Appointment of Directors}

\item
  The charity may by ordinary resolution:
  \begin{enumerate}
  \item
    appoint a person who is willing to act to be a director; and
  \item
    determine the rotation in which any additional directors are to
    retire.
  \end{enumerate}

\item
  No person other than a director retiring by rotation may be
  appointed a director at any general meeting unless:
  \begin{enumerate}
  \item
    he or she is recommended for re-election by the directors; or
  \item
    not less than fourteen nor more than thirty-five clear days before
    the date of the meeting, the charity is given a notice that:
    \begin{enumerate}
    \item
      is signed by a member entitled to vote at the meeting;
    \item
      states the member's intention to propose the appointment of a
      person as a director;
    \item
      contains the details that, if the person were to be appointed, the
      charity would have to file at Companies House; and
    \item
      is signed by the person who is to be proposed to show his or her
      willingness to be appointed.
    \end{enumerate}
  \end{enumerate}
\item
  All members who are entitled to receive notice of a general meeting
  must be given not less than seven nor more than twenty-eight clear
  days' notice of any resolution to be put to the meeting to appoint
  a director other than a director who is to retire by rotation.

\item
  \begin{enumerate}
  \item
    The directors may appoint a person who is willing to act to be a
    director.
  \item
    A director appointed by a resolution of the other directors must
    retire at the next annual general meeting and must not be taken
    into account in determining the directors who are to retire by
    rotation.
  \end{enumerate}
\item
  The appointment of a director, whether by the charity in general
  meeting or by the other directors, must not cause the number of
  directors to exceed any number fixed as the maximum number of
  directors.

\section{Disqualification and Removal of Directors}

\item \label{director-cease}
  A director shall cease to hold office if he or she:
  \begin{enumerate}
    \item
    ceases to be a director by virtue of any provision in the
    Companies Acts or is prohibited by law from being a director; 
    \item
    is disqualified from acting as a trustee by virtue of section 72 of
    the Charities Act 1993 (or any statutory re-enactment or
    modification of that provision);
    \item
    ceases to be a member of the charity; 
    \item
    becomes incapable by reason of mental disorder, illness
    or injury of managing and administering his or her own affairs;
    \item 
    resigns as a director by notice to the charity (but only if at
    least two directors will remain in office when the notice of
    resignation is to take effect); or 
    \item 
    is absent without the
    permission of the directors from all their meetings held within a
    period of six consecutive months and the directors resolve that his
    or her office be vacated.
  \end{enumerate}

\section{Remuneration of Directors}

\item
  The directors must not be paid any remuneration unless it is
  authorised by article \ref{cls:income-property}.

\section{Proceedings of Directors}

\item
  \begin{enumerate}
  \item
    The directors may regulate their proceedings as they think fit,
    subject to the provisions of the articles.
  \item
    Any director may call a meeting of the directors.
  \item
    The secretary (if any) must call a meeting of the directors if
    requested to do so by a director.
  \item
    Questions arising at a meeting shall be decided by a majority of
    votes.
  \item
    In the case of an equality of votes, the person who is chairing the
    meeting shall have a second or casting vote.
  \item
    A meeting may be held by suitable electronic means agreed by the
    directors in which each participant may communicate with all the
    other participants.
  \end{enumerate}
\item
  \begin{enumerate}
  \item
    No decision may be made by a meeting of the directors unless a
    quorum is present at the time the decision is purported to be made.
    `Present' includes being present by suitable electronic means
    agreed by the directors in which a participant or participants may
    communicate with all the other participants.
  \item
    The quorum shall be two or the number nearest to one-third of the
    total number of directors, whichever is the greater, or such larger
    number as may be decided from time to time by the directors.
  \item
    A director shall not be counted in the quorum present when any
    decision is made about a matter upon which that director is not
    entitled to vote.
  \end{enumerate}
\item
  If the number of directors is less than the number fixed as the
  quorum, the continuing directors or director may act only for the
  purpose of filling vacancies or of calling a general meeting.
\item
  \begin{enumerate}
  \item
    The directors shall appoint a director to chair their meetings and
    may at any time revoke such appointment.
  \item
    If no-one has been appointed to chair meetings of the directors or
    if the person appointed is unwilling to preside or is not present
    within ten minutes after the time appointed for the meeting, the
    directors present may appoint one of their number to chair that
    meeting.
  \item
    The person appointed to chair meetings of the directors shall have
    no functions or powers except those conferred by the articles or
    delegated to him or her by the directors.
  \end{enumerate}
\item
  \begin{enumerate}
  \item
    A resolution in writing or in electronic form agreed by all of the
    directors entitled to receive notice of a meeting of the directors
    and to vote upon the resolution shall be as valid and effectual as
    if it had been passed at a meeting of the directors duly convened
    and held.
  \item
    The resolution in writing may comprise several documents containing
    the text of the resolution in like form to each of which one or
    more directors has signified their agreement.
  \end{enumerate}

\section{Delegation}

\item
  \begin{enumerate}
  \item
    The directors may delegate any of their powers or functions to a
    committee of two or more directors but the terms of any delegation
    must be recorded in the minute book.
  \item
    The directors may impose conditions when delegating, including the
    conditions that:
    \begin{enumerate}
    \item
      the relevant powers are to be exercised exclusively by the
      committee to whom they delegate;
    \item
      no expenditure may be incurred on behalf of the charity except in
      accordance with a budget previously agreed with the directors.
    \end{enumerate}
  \item
    The directors may revoke or alter a delegation.
  \item
    All acts and proceedings of any committees must be fully and
    promptly reported to the directors.
  \end{enumerate}

\section{Declaration of Directors' Interests}

\item \label{directors-interests}
  A director must declare the nature and extent of any interest,
  direct or indirect, which he or she has in a proposed transaction
  or arrangement with the charity or in any transaction or
  arrangement entered into by the charity which has not previously
  been declared. A director must absent himself or herself from any
  discussions of the directors in which it is possible that a
  conflict will arise between his or her duty to act solely in the
  interests of the charity and any personal interest (including but
  not limited to any personal financial interest).

\section{Conflicts of Interests}

\item 
  \begin{enumerate}
  \item
    If a conflict of interests arises for a director because of a duty
    of loyalty owed to another organisation or person and the conflict
    is not authorised by virtue of any other provision in the articles,
    the unconflicted directors may authorise such a conflict of
    interests where the following conditions apply:
    \begin{enumerate}
    \item
      the conflicted director is absent from the part of the meeting at
      which there is discussion of any arrangement or transaction
      affecting that other organisation or person;
    \item
      the conflicted director does not vote on any such matter and is not
      to be counted when considering whether a quorum of directors is
      present at the meeting; and
    \item
      the unconflicted directors consider it is in the interests of the
      charity to authorise the conflict of interests in the circumstances
      applying.
    \end{enumerate}
  \item \label{conflict-interest-loyalty}
    In this article a conflict of interests arising because of a duty
    of loyalty owed to another organisation or person only refers to
    such a conflict which does not involve a direct or indirect benefit
    of any nature to a director or to a connected person.
  \end{enumerate}

\section{Validity of Directors' Decisions}

\item
  \begin{enumerate}
  \item \label{directors-validity}
    Subject to article \ref{directors-validity-void}, all acts done by a meeting of directors,
    or of a committee of directors, shall be valid notwithstanding the
    participation in any vote of a director:
    \begin{enumerate}
    \item
      who was disqualified from holding office;
    \item
      who had previously retired or who had been obliged by the
      constitution to vacate office;
    \item
      who was not entitled to vote on the matter, whether by reason of a
      conflict of interests or otherwise; if without:
    \item
      the vote of that director; and
    \item
      that director being counted in the quorum; the decision has been
      made by a majority of the directors at a quorate meeting.
    \end{enumerate}
  \item \label{directors-validity-void}
    Article \ref{directors-validity} does not permit a director or a connected person to
    keep any benefit that may be conferred upon him or her by a
    resolution of the directors or of a committee of directors if, but
    for article \ref{directors-validity}, the resolution would have been void, or if the
    director has not complied with article \ref{directors-interests}.
  \end{enumerate}

\section{Seal}

\item
  If the charity has a seal it must only be used by the authority of
  the directors or of a committee of directors authorised by the
  directors. The directors may determine who shall sign any
  instrument to which the seal is affixed and unless otherwise so
  determined it shall be signed by a director and by the secretary
  (if any) or by a second director.

\section{Minutes}

\item
  The directors must keep minutes of all:
  \begin{enumerate}
  \item
    appointments of officers made by the directors;
  \item
    proceedings at meetings of the charity;
  \item
    meetings of the directors and committees of directors including:
    \begin{enumerate}
    \item
      the names of the directors present at the meeting;
    \item
      the decisions made at the meetings; and
    \item
      where appropriate the reasons for the decisions.
    \end{enumerate}
  \end{enumerate}

\section{Accounts}

\item
  \begin{enumerate}
  \item
    The directors must prepare for each financial year accounts as
    required by the Companies Acts. The accounts must be prepared to
    show a true and fair view and follow accounting standards issued or
    adopted by the Accounting Standards Board or its successors and
    adhere to the recommendations of applicable Statements of
    Recommended Practice.
  \item
    The directors must keep accounting records as required by the
    Companies Acts.
  \end{enumerate}

\section{Annual Report and Return and Register of Charities}

\item
  \begin{enumerate}
  \item
    The directors must comply with the requirements of the Charities
    Act 1993 with regard to the:
    \begin{enumerate}
    \item
      transmission of a copy of the statements of account to the
      Commission;
    \item
      preparation of an Annual Report and the transmission of a copy of
      it to the Commission;
    \item
      preparation of an Annual Return and its transmission to the
      Commission.
    \end{enumerate}
  \item
    The directors must notify the Commission promptly of any changes to
    the charity's entry on the Central Register of Charities.
  \end{enumerate}

\section{Means of Communication to be Used}

\item
  \begin{enumerate}
  \item
    Subject to the articles, anything sent or supplied by or to the
    charity under the articles may be sent or supplied in any way in
    which the Companies Act 2006 provides for documents or information
    which are authorised or required by any provision of that Act to be
    sent or supplied by or to the charity.
  \item
    Subject to the articles, any notice or document to be sent or
    supplied to a director in connection with the taking of decisions
    by directors may also be sent or supplied by the means by which
    that director has asked to be sent or supplied with such notices or
    documents for the time being.
  \end{enumerate}
\item
  Any notice to be given to or by any person pursuant to the
  articles:
  \begin{enumerate}
  \item
    must be in writing; or
  \item
    must be given in electronic form.
  \end{enumerate}

\item
  \begin{enumerate}
  \item
    The charity may give any notice to a member either:
    \begin{enumerate}
    \item
      personally; or
    \item
      by sending it by post in a prepaid envelope addressed to the member
      at his or her address; or
    \item
      by leaving it at the address of the member; or
    \item
      by giving it in electronic form to the member's address.
    \item
      by placing the notice on a website and providing the person with a
      notification in writing or in electronic form of the presence of
      the notice on the website. The notification must state that it
      concerns a notice of a company meeting and must specify the place
      date and time of the meeting.
    \end{enumerate}
  \item
    A member who does not register an address with the charity or who
    registers only a postal address that is not within the United
    Kingdom shall not be entitled to receive any notice from the
    charity.
  \end{enumerate}
\item
  A member present in person at any meeting of the charity shall be
  deemed to have received notice of the meeting and of the purposes
  for which it was called.

\item
  \begin{enumerate}
  \item
    Proof that an envelope containing a notice was properly addressed,
    prepaid and posted shall be conclusive evidence that the notice was
    given.
  \item
    Proof that an electronic form of notice was given shall be
    conclusive where the company can demonstrate that it was properly
    addressed and sent, in accordance with section 1147 of the
    Companies Act 2006.
  \item
    In accordance with section 1147 of the Companies Act 2006, notice
    shall be deemed to be given:
    \begin{enumerate}
    \item
      48 hours after the envelope containing it was posted; or
    \item
      in the case of an electronic form of communication, 48 hours after
      it was sent.
    \end{enumerate}
  \end{enumerate}

\section{Indemnity}

\item \label{cls:directors-indemnity}
  \begin{enumerate}
  \item
    The charity shall indemnify any director against any
    liability incurred by him or her or it in that capacity, to the
    extent permitted by sections 232 to 234 of the Companies Act 2006.
  \item
    In this article a ``relevant director'' means any director or
    former director of the charity.
  \end{enumerate}

\section{Rules}

\item
  \begin{enumerate}
  \item
    The directors may from time to time make such reasonable and proper
    rules or bye laws as they may deem necessary or expedient for the
    proper conduct and management of the charity.
  \item
    The bye laws may regulate the following matters but are not
    restricted to them:
    \begin{enumerate}
    \item
      the admission of members of the charity (including the admission of
      organisations to membership) and the rights and privileges of such
      members, and the entrance fees, subscriptions and other fees or
      payments to be made by members;
    \item
      the conduct of members of the charity in relation to one another,
      and to the charity's employees and volunteers;
    \item
      the setting aside of the whole or any part or parts of the
      charity's premises at any particular time or times or for any
      particular purpose or purposes;
    \item
      the procedure at general meetings and meetings of the directors in
      so far as such procedure is not regulated by the Companies Acts or
      by the articles;
    \item
      generally, all such matters as are commonly the subject matter of
      company rules.
    \end{enumerate}
  \item
    The charity in general meeting has the power to alter, add to or
    repeal the rules or bye laws.
  \item
    The directors must adopt such means as they think sufficient to
    bring the rules and bye laws to the notice of members of the
    charity.
  \item
    The rules or bye laws shall be binding on all members of the
    charity. No rule or bye law shall be inconsistent with, or shall
    affect or repeal anything contained in, the articles.
  \end{enumerate}

\section{Dissolution}

\item
  \begin{enumerate}
  \item \label{dissolve-transfer}
    The members of the charity may at any time before, and in
    expectation of, its dissolution resolve that any net assets of the
    charity after all its debts and liabilities have been paid, or
    provision has been made for them, shall on or before the
    dissolution of the charity be applied or transferred in any of the
    following ways:
    \begin{enumerate}
    \item
      directly for the Objects; or
    \item
      by transfer to any charity or charities for purposes similar to the
      Objects; or
    \item
      to any charity or charities for use for particular purposes that
      fall within the Objects.
    \end{enumerate}
  \item
    Subject to any such resolution of the members of the charity, the
    directors of the charity may at any time before and in expectation
    of its dissolution resolve that any net assets of the charity after
    all its debts and liabilities have been paid, or provision made for
    them, shall on or before dissolution of the charity be applied or
    transferred:
    \begin{enumerate}
    \item
      directly for the Objects; or
    \item
      by transfer to any charity or charities for purposes similar to the
      Objects; or
    \item
      to any charity or charities for use for particular purposes that
      fall within the Objects.
    \end{enumerate}
  \item
    In no circumstances shall the net assets of the charity be paid to
    or distributed among the members of the charity (except to a member
    that is itself a charity) and if no resolution in accordance with
    article \ref{dissolve-transfer} is passed by the members or the directors the net
    assets of the charity shall be applied for charitable purposes as
    directed by the Court or the Commission.
  \end{enumerate}
\end{enumerate}

### 2011-06-01 constitution/articles-body.tex
Use the description environment (still looks a bit tatty...)

@@
   In the articles:
-  \begin{itemize}
-  \item
-    ``address'' means a postal address or, for the purposes of
+  \begin{description}
+  \item[Address] means a postal address or, for the purposes of
     electronic communication, a fax number, an e-mail or postal address
     or a telephone number for receiving text messages in each case
-    registered with the charity;
-  \item
-    ``the articles'' means the charity's articles of association;
-  \item
-    ``the charity'' means the company intended to be regulated by the
-    articles;
-  \item
-    ``clear days'' in relation to the period of a notice means a period
+    registered with the charity
+  \item[The Articles] means the charity's articles of association
+  \item[The Charity] means the company intended to be regulated by the
+    articles
+  \item[Clear days] in relation to the period of a notice means a period
     excluding:
@@
     \item
-      the day for which it is given or on which it is to take effect;
+      the day for which it is given or on which it is to take effect
     \end{itemize}
-  \item
-    ``the Commission'' means the Charity Commission for England and
-    Wales;
-  \item
-    ``Companies Acts'' means the Companies Acts (as defined in section
-    2 of the Companies Act 2006) insofar as they apply to the charity;
-  \item
-    ``the directors'' means the directors of the charity. The directors
+  \item[The Commission] means the Charity Commission for England and Wales
+  \item[Companies Acts] means the Companies Acts (as defined in section
+    2 of the Companies Act 2006) insofar as they apply to the charity
+  \item[The Directors] means the directors of the charity. The directors
     are charity trustees as defined by section 97 of the Charities Act
-    1993;
-  \item
-    ``document'' includes, unless otherwise specified, any document
-    sent or supplied in electronic form;
-  \item
-    ``electronic form'' has the meaning given in section 1168 of
-    theCompanies Act 2006;
-  \item
-    ``the memorandum'' means the charity's memorandum of association;
-  \item
-    ``officers'' includes the directors and the secretary (if any);
-  \item
-    ``the seal'' means the common seal of the charity if it has one;
-  \item
-    ``secretary'' means any person appointed to perform the duties of
-    the secretary of the charity;
-  \item
-    ``the United Kingdom'' means Great Britain and Northern Ireland;
-    and
-  \item
-    words importing one gender shall include all genders, and the
-    singular includes the plural and vice versa.
-  \end{itemize}
+    1993
+  \item[Document] includes, unless otherwise specified, any document
+    sent or supplied in electronic form
+  \item[Electronic Form] has the meaning given in section 1168 of the Companies Act 2006
+  \item[The Memorandum] means the charity's memorandum of association
+  \item[Officers] includes the directors and the secretary (if any)
+  \item[The seal] means the common seal of the charity if it has one
+  \item[Secretary] means any person appointed to perform the duties of
+    the secretary of the charity
+  \item[The United Kingdom] means Great Britain and Northern Ireland.
+  \end{description}
+  Words importing one gender shall include all genders, and the singular
+  includes the plural and vice versa.
+
   Unless the context otherwise requires words or expressions

### 2011-07-16 constitution/articles-body.tex
One Click Orgs phase one clause

@@
     \item
-    The directors may regulate their proceedings as they think fit,
-    subject to the provisions of the articles.
-  \item
-    Any director may call a meeting of the directors.
-  \item
-    The secretary (if any) must call a meeting of the directors if
-    requested to do so by a director.
-  \item
-    Questions arising at a meeting shall be decided by a majority of
-    votes.
-  \item
-    In the case of an equality of votes, the person who is chairing the
-    meeting shall have a second or casting vote.
-  \item
-    A meeting may be held by suitable electronic means agreed by the
-    directors in which each participant may communicate with all the
-    other participants.
-  \end{enumerate}
-\item
-  \begin{enumerate}
-  \item
-    No decision may be made by a meeting of the directors unless a
-    quorum is present at the time the decision is purported to be made.
-    `Present' includes being present by suitable electronic means
-    agreed by the directors in which a participant or participants may
-    communicate with all the other participants.
-  \item
-    The quorum shall be two or the number nearest to one-third of the
-    total number of directors, whichever is the greater, or such larger
-    number as may be decided from time to time by the directors.
-  \item
-    A director shall not be counted in the quorum present when any
-    decision is made about a matter upon which that director is not
-    entitled to vote.
-  \end{enumerate}
-\item
-  If the number of directors is less than the number fixed as the
-  quorum, the continuing directors or director may act only for the
-  purpose of filling vacancies or of calling a general meeting.
-\item
-  \begin{enumerate}
-  \item
-    The directors shall appoint a director to chair their meetings and
-    may at any time revoke such appointment.
-  \item
-    If no-one has been appointed to chair meetings of the directors or
-    if the person appointed is unwilling to preside or is not present
-    within ten minutes after the time appointed for the meeting, the
-    directors present may appoint one of their number to chair that
-    meeting.
-  \item
-    The person appointed to chair meetings of the directors shall have
-    no functions or powers except those conferred by the articles or
-    delegated to him or her by the directors.
-  \end{enumerate}
-\item
-  \begin{enumerate}
-  \item
-    A resolution in writing or in electronic form agreed by all of the
-    directors entitled to receive notice of a meeting of the directors
-    and to vote upon the resolution shall be as valid and effectual as
-    if it had been passed at a meeting of the directors duly convened
-    and held.
-  \item
-    The resolution in writing may comprise several documents containing
-    the text of the resolution in like form to each of which one or
-    more directors has signified their agreement.
+    The Directors may from time to time specify a web based system (``the
+    Governance System'') for recording and managing their decision making process.
+    \item
+    The Governance System must:
+        \begin{enumerate}
+            \item
+             permit any director to create a proposal that is then available for viewing (on
+             presentation of suitable credentials) by all directors and any member of the
+             Association;
+            \item
+            after a proposal has been created, send it promptly to each director's email address;
+            \item
+             maintain one or more rules as to the period (``the voting period'') within which any
+             proposal must be accepted or rejected, which may vary from proposal to proposal;
+            \item
+             during the voting period, permit any director to indicate whether they accept or reject
+             the proposal;
+            \item
+             record the votes cast by each director;
+            \item
+             record that a proposal has been ``passed'' if the requisite number of directors have
+             indicated their acceptance of the proposal via the governance system;
+            \item
+             permit the recording of minutes; and
+            \item
+             maintain a current contact email address for each director (``the director's email
+             address'').
+        \end{enumerate}
+    \item
+    Any proposal that has been recorded as ``passed'' by the Governance System shall
+    be treated as a decision of the directors.
+    \item
+    The Governance System to be used on the adoption of these articles shall be that
+    supplied by One Click Orgs and accessed on the World Wide Web at the address
+    http://london-gov.hackspace.org.uk
+  \end{enumerate}
+
+\item
+  \begin{enumerate}
+    \item
+    Decisions of the directors may be made either:
+    \begin{enumerate}
+        \item
+        by the use of the Governance System; or
+        \item
+        by a written resolution in accordance with the procedure described below.
+    \end{enumerate}
+    \item
+    All directors' decisions must be made in one of these two ways, and a decision
+    made in any other way will be ineffective.
+    \item
+    The requisite number of directors who must accept a proposal made using the
+    Governance System or a written resolution before it is passed is [a majority of the
+    number of directors for the time being].
+  \end{enumerate}
+
+\item
+    A written resolution may be passed if:
+    \begin{enumerate}
+        \item
+        the text of the resolution is circulated to all directors in writing; and
+        \item
+        the requisite number of directors have given to all the other directors in writing their
+        agreement to the text of the resolution.
     \end{enumerate}

### 2011-07-16 constitution/articles-body.tex
Some more OCO stuff I missed. General tidying up.

@@
   \item
-    to provide and maintain shared community workspace and equipment for the use of the residents of London.
+    to provide and maintain shared community workspace and equipment in London.
   \end{enumerate}
@@
       partnership with the director or with any person falling within
-      paragraph (i) or (ii)above;
+      paragraph (i) or (ii) above;
     \item
@@
     any sum due from the member to the charity is not paid in full
-    within six months of it falling due;
+    within two weeks of it falling due;
   \item
@@
 \section{General Meetings}
-
-\item
-  \begin{enumerate}
-  \item
-    The charity must hold its first annual general meeting within
-    eighteen months after the date of its incorporation.
-  \item
-    An annual general meeting must be held in each subsequent year and
-    not more than fifteen months may elapse between successive annual
-    general meetings.
-  \end{enumerate}
-\item
-  The directors may call a general meeting at any time.
+\item
+    The Board may convene a General Meeting whenever they think fit.
+
+\item 
+    General Meetings shall also be convened on such requisition, or in default may be convened by such
+    requisitionists, as provided by section 304 of the Companies Act 2006.
 
@@
         agreement to the text of the resolution.
+    \end{enumerate}
+
+\item
+    \begin{enumerate}
+    \item
+        The directors may delegate any of their powers or functions concerning the day
+        to day management of the affairs of the Company to any person or persons as they may
+        from time to time select.
+    \item
+        All acts done by a director shall, even if it is afterwards discovered that there was
+        a defect in their appointment or that they were disqualified from holding office or had
+        vacated office, be as valid as if such person had been duly appointed and was qualified
+        and had continued to be a director.
+    \item
+        Where on any particular occasion more than 2 directors, in the course of their
+        office as directors, discuss the affairs of the Company by any means, whether in person
+        or otherwise, a minute shall be made and recorded indicating:
+            \begin{enumerate}
+                \item
+                    when the discussion took place;
+                \item
+                    the identities of the directors involved; and
+                \item
+                    the identities of the directors involved; and
+            \end{enumerate}
+    \item
+        Minutes of directors meetings:
+            \begin{enumerate}
+                \item
+                    may be held in electronic form, and in particular using the Governance System;
+                \item
+                    must be held for ten years from the date of the discussion in accordance with section
+                    248 of the Companies Act 2006.
+            \end{enumerate}
     \end{enumerate}
@@
 
-\section{Minutes}
-
-\item
-  The directors must keep minutes of all:
-  \begin{enumerate}
-  \item
-    appointments of officers made by the directors;
-  \item
-    proceedings at meetings of the charity;
-  \item
-    meetings of the directors and committees of directors including:
-    \begin{enumerate}
-    \item
-      the names of the directors present at the meeting;
-    \item
-      the decisions made at the meetings; and
-    \item
-      where appropriate the reasons for the decisions.
-    \end{enumerate}
-  \end{enumerate}
-
 \section{Accounts}
@@
 
-\section{Annual Report and Return and Register of Charities}
+\section{Annual Report and Register of Charities}
 
@@
     Proof that an electronic form of notice was given shall be
-    conclusive where the company can demonstrate that it was properly
-    addressed and sent, in accordance with section 1147 of the
-    Companies Act 2006.
+    conclusive where the company can demonstrate that it was
+    accepted by an electronic mail host for that address
   \item

### 2011-07-20 constitution/articles-body.tex
Specify a quorum of 10

@@
     \begin{enumerate}
-    \item x members present in person or by proxy and entitled to vote upon
+    \item 10 members present in person or by proxy and entitled to vote upon
       the business to be conducted at the meeting; or
@@
   \item
-    If :
+    If:
     \begin{enumerate}
@@
   \begin{enumerate}
-  \item
     A director must be a natural person aged 16 years or older.
@@
 
-\section{Seal}
-
-\item
-  If the charity has a seal it must only be used by the authority of
-  the directors or of a committee of directors authorised by the
-  directors. The directors may determine who shall sign any
-  instrument to which the seal is affixed and unless otherwise so
-  determined it shall be signed by a director and by the secretary
-  (if any) or by a second director.
-
 \section{Accounts}

### 2011-07-20 constitution/articles-body.tex
Specify a maximum number of directors.
Alter quorum for general meetings. 1/10th of membership is actually quite large.

@@
   \item
-    A quorum is:
-    \begin{enumerate}
-    \item 10 members present in person or by proxy and entitled to vote upon
-      the business to be conducted at the meeting; or
-    \item
-      one tenth of the total membership at the time
-    \end{enumerate}
+    A quorum is 10 members present in person or by proxy and entitled to vote upon
+      the business to be conducted at the meeting.
   \item
@@
 \item
-  The number of directors shall be not less than three but (unless
-  otherwise determined by ordinary resolution) shall not be subject
-  to any maximum.
+  The number of directors shall be not less than three, nor more than eight.
 

### 2011-07-21 constitution/articles-body.tex
Remove placeholder for directors majority

@@
     \item
-    The requisite number of directors who must accept a proposal made using the
-    Governance System or a written resolution before it is passed is [a majority of the
-    number of directors for the time being].
+    A majority of the directors must accept a proposal made using the
+    Governance System or a written resolution before it is passed.
   \end{enumerate}

### 2011-07-25 constitution/articles-body.tex
Remove definition ambiguity

@@
     registered with the charity
-  \item[The Articles] means the charity's articles of association
-  \item[The Charity] means the company intended to be regulated by the
-    articles
+  \item[The Articles] means these articles of association
   \item[Clear days] in relation to the period of a notice means a period
@@
   \item[Electronic Form] has the meaning given in section 1168 of the Companies Act 2006
-  \item[The Memorandum] means the charity's memorandum of association
   \item[Officers] includes the directors and the secretary (if any)
-  \item[The seal] means the common seal of the charity if it has one
   \item[Secretary] means any person appointed to perform the duties of
     the secretary of the charity
-  \item[The United Kingdom] means Great Britain and Northern Ireland.
   \end{description}

### 2011-07-26 constitution/articles-body.tex
Add Minutes section

@@
 
+\section{Minutes}
+
+\item
+The directors must keep minutes of all:
+    \begin{enumerate}
+        \item
+            appointments of officers made by the directors;
+        \item
+            proceedings at meetings of the charity;
+        \item
+            meetings of the directors and committees of directors including:
+            \begin{enumerate}
+                \item
+                    the names of the directors present at the meeting;
+                \item
+                    the decisions made at the meetings; and
+                \item
+                    where appropriate the reasons for the decisions.
+            \end{enumerate}
+    \end{enumerate}
+
 \section{Accounts}

### 2011-07-26 constitution/articles-body.tex
Add "Disputes" clause as per new GD1

@@
 
+\section{Disputes}
+
+\item
+    If a dispute arises between members of the company about the validity
+    or propriety of anything done by the members of the company under these
+    articles, and the dispute cannot be resolved by agreement, the parties
+    to the dispute must first try in good faith to settle the dispute by
+    mediation before resorting to litigation.
+
 \section{Dissolution}

### 2011-07-26 constitution/articles-body.tex
Make directors' conflict-of-interest rules in line with latest CC GD1

@@
   \item
-    to provide and maintain shared community workspace and equipment in London.
+    to provide and maintain shared community workspace and equipment in Greater London.
   \end{enumerate}
@@
   \item
-    None of the income or property of the charity may be paid or
+    Subject to article \ref{cls:benefits-payments}, none of the income or 
+    property of the charity may be paid or
     transferred directly or indirectly by way of dividend bonus or
@@
     \end{enumerate}
+  \end{enumerate}
+
+\section{Benefits and Payments to Charity Directors and Connected Persons}
+
+\item
+  \subsection{General provisions}
+  \label{cls:benefits-payments}
+  \begin{enumerate}
   \item
@@
         the directors obtain the prior written approval of the Commission
-        and fully comply with any procedures it prescribes. In this article
+        and fully comply with any procedures it prescribes. 
+      \end{enumerate}
+        In this article
         a `financial benefit' means a benefit, direct or indirect, which is
@@
     \end{enumerate}
-    \end{enumerate}
-  \item
+
+  \item
+    \subsection{Scope and powers permitting directors’ or connected persons’ benefits}
     \label{scls:directors-scope}
@@
     \item
-      The directors may arrange for the purchase, out of the funds of the
-      charity, of insurance designed to indemnify the directors in
-      accordance with the terms of, and subject to the conditions in,
-      section 73F of the Charities Act 1993.
-    \end{enumerate}
-  \item \label{goods}
+      A director or connected person may take part in the
+      normal trading and fundraising activities of the charity on
+      the same terms as members of the public.
+    \end{enumerate}
+  \item 
+    \subsection{Payment for supply of goods only – controls}
+    \label{goods}
     \label{scls:supply-goods} The charity and its directors may only
@@
   \item \label{def-charity}
-    In sub-clauses \ref{scls:director-reimburse} to \ref{goods}, ``charity'' shall include
+    In sub-clauses \ref{scls:directors-scope} to \ref{goods}, ``charity'' shall include
     any company in which the charity:
@@
     \end{itemize}
-  \item \label{def-connected}
-    In sub-clauses \ref{scls:directors-remuneration} to \ref{goods}, \ref{conflict-interest-loyalty},
-    and \ref{directors-validity-void} ``connected person'' means:
-    \begin{enumerate}
-    \item
-      \label{art:connected-child} a child, parent, grandchild,
-      grandparent, brother or sister of the director;
-    \item
-      \label{art:connected-spouse} the spouse or civil partner of the
-      director or of any person falling within paragraph (i) above;
-    \item
-      \label{art:connected-business} a person carrying on business in
-      partnership with the director or with any person falling within
-      paragraph (i) or (ii) above;
-    \item
-      an institution which is controlled –
-      \begin{enumerate}
-      \item
-        by the director or any connected person falling within paragraph (i) to (iii) above; or
-      \item
-        by two or more persons falling within sub-paragraph (A), when taken
-        together
-      \end{enumerate}
-    \item
-      a body corporate in which –
-      \begin{enumerate}
-        \item
-            the director or any connected person falling within paragraphs (i) to (iii) has a substantial interest; or
-        \item
-            two or more persons falling within sub-paragraph (A) who, when
-            taken together, have a substantial interest.
-      \end{enumerate}
-    \end{enumerate}
-  \item
-    For the purposes of interpreting the terms used in sub-clauses \ref{def-charity}
-    and \ref{def-connected}, paragraphs 2 to 4 of Schedule 5 to the Charities Act 1993
-    apply.
   \end{enumerate}
@@
   \end{enumerate}
-\end{enumerate}
+
+\section{Interpretation}
+
+\item \label{def-connected}
+    In articles \ref{cls:benefits-payments}, \ref{conflict-interest-loyalty},
+    and \ref{directors-validity-void} ``connected person'' means:
+    \begin{enumerate}
+    \item
+      \label{art:connected-child} a child, parent, grandchild,
+      grandparent, brother or sister of the director;
+    \item
+      \label{art:connected-spouse} the spouse or civil partner of the
+      director or of any person falling within paragraph (a) above;
+    \item
+      \label{art:connected-business} a person carrying on business in
+      partnership with the director or with any person falling within
+      paragraph (a) or (b) above;
+    \item
+      an institution which is controlled –
+      \begin{enumerate}
+      \item
+        by the director or any connected person falling within paragraph (a) to (c) above; or
+      \item
+        by two or more persons falling within sub-paragraph (i), when taken
+        together
+      \end{enumerate}
+    \item
+      a body corporate in which –
+      \begin{enumerate}
+        \item
+            the director or any connected person falling within paragraphs (a) to (c) has a substantial interest; or
+        \item
+            two or more persons falling within sub-paragraph (i) who, when
+            taken together, have a substantial interest.
+        \item
+            Paragraphs 2 to 4 of Schedule 5 to the Charities Act 1993 apply for the
+            purposes of interpreting the terms used in this sub-clause.
+        \end{enumerate}
+    \end{enumerate}
+\end{enumerate}

### 2011-12-29 annualreports/2011/balancesheet.tex
2011 annual report, as submitted to Companies House

@@
 {\bf Fixed Assets}                              &        &       &       &       \\
-{\bf Tangible fixed assets}                     &       & 5,337 &       & 1,054 \\
+{\bf Tangible fixed assets}                     &        & 5,525 &       & 1,040 \\
 \cmidrule(r){2-3} \cmidrule(r){4-5} \\
@@
 Rental Deposit                                  & 7,696  &       &       &       \\
-Cash at bank and in hand                        & 7,568 &       & 8,642 &       \\
-Creditors: amounts falling due within one year  & -1,979 &      & -1,343&      \\
-{\bf Net current assets}                        &       & 13,285&       & 7,299 \\
+Cash at bank and in hand                        & 7,688  &       & 8,642 &       \\
+Creditors: amounts falling due within one year  & -2,511 &       & -1,343&      \\
+Prepaid Subscriptions                           & -610   &       &       &      \\
+{\bf Net current assets}                        &        & 20,908 &       & 7,285 \\
 \cmidrule(r){2-3} \cmidrule(r){4-5} \\
-{\bf Total assets less current liabilities}     &       & 18,622&       & 8,354 \\
+{\bf Total assets less current liabilities}     &        & 17,787 &       & 8,339 \\
 \cmidrule(r){2-3} \cmidrule(r){4-5}  \\
 {\bf Capital and Reserves}&\\
-Income and expenditure account                  &       & 10,269&       & 8,354 \\
+Income and expenditure account                  &        & 10,267 &       & 8,339 \\
 \bottomrule
@@
 
-{\footnotesize For the financial period ended 31 March 2010 the
+{\footnotesize For the financial period ended 31 March 2011 the
 company was entitled to exemption from audit under section 477 of the
@@
 
-Approved by the Board for issue on <date>
+Approved by the Board for issue on the 28\superscript{th} of December 2011
 \vspace{48pt}

### 2011-12-29 annualreports/2011/notes.tex
2011 annual report, as submitted to Companies House

--- 2010-10-02 annualreports/2010/notes.tex
@@
                 \toprule
-                Fixtures \& Fittings & Over 3 years at 33\% per annum on a straight line basis \\
-                Plant \& Machinery & Over 3 years at 33\% per annum on a straight line basis \\
+                Fixtures \& Fittings & Over 5 years at 20\% per annum on a straight line basis \\
+                Plant \& Machinery & Over 4 years at 25\% per annum on a straight line basis \\
                 \bottomrule
@@
     \end{enumerate}
+    \item {\bf Change of depreciation policy} \label{depreciation_change} \\ 
+        The directors have chosen to alter the depreciation policy to be more in line
+        with the expected useful life of equipment, fixtures, and fittings, based on
+        observations made in the last year. Fixtures and Fittings are now depreciated
+        over five years, and plant and machinery over four years on a straight-line
+        basis.
+
+        For the 2010/11 reporting period, these changes have resulted in the
+        depreciation charge being reduced from £1,325 to £952, which represents a 4\%
+        increase of the operating surplus.
+
+        The depreciation expenditure for the 2009-2010 financial year has been restated
+        according to the new depreciation policy. This has resulted in a change of £13
+        to the depreciation line, or less than 1\% of the surplus for that year.
+
 \end{enumerate}

### 2012-09-30 constitution/articles-body.tex
Less/fewer
Change this to three to be consistent with the minimum number of directors.
Update to remove charity reference.
* Replace all refs to "charity" with "association".
* Remove references to the Charities Act.
* Remove extensive and complex "connected persons" wording.

--- 2011-07-26 constitution/articles-body.tex
@@
-\title{Articles of Association of London Hackspace Ltd.}
-\begin{enumerate}
-\item
-  The company's name is London Hackspace Ltd. (and in this document
-  it is called the ``charity'').
-
+\title{Articles of Association of London Hackspace Ltd}
+\begin{enumerate}
 \section{Interpretation}
-
 \item
@@
   \begin{description}
+  \item[the association] the above-named association.
   \item[Address] means a postal address or, for the purposes of
@@
     or a telephone number for receiving text messages in each case
-    registered with the charity
+    registered with the association
   \item[The Articles] means these articles of association
@@
     \end{itemize}
-  \item[The Commission] means the Charity Commission for England and Wales
   \item[Companies Acts] means the Companies Acts (as defined in section
-    2 of the Companies Act 2006) insofar as they apply to the charity
-  \item[The Directors] means the directors of the charity. The directors
-    are charity trustees as defined by section 97 of the Charities Act
-    1993
-  \item[Document] includes, unless otherwise specified, any document
-    sent or supplied in electronic form
+    2 of the Companies Act 2006) insofar as they apply to the association
+  \item[The Directors] means the directors of the association.
+  \item[Document] includes, unless otherwise specified, any document sent or supplied in electronic form
   \item[Electronic Form] has the meaning given in section 1168 of the Companies Act 2006
@@
   \item[Secretary] means any person appointed to perform the duties of
-    the secretary of the charity
+    the secretary of the association.
   \end{description}
@@
 
-  Unless the context otherwise requires words or expressions
+  Unless the context otherwise requires, words or expressions
   contained in the articles have the same meaning as in the Companies
-  Acts but excluding any statutory modification not in force when
-  this constitution becomes binding on the charity.
+  Acts as in force on the date when these Articles become binding
+  on the association.
 
@@
 \item
-  The liability of the members is limited to a sum not exceeding £1,
-  being the amount that each member undertakes to contribute to the
-  assets of the charity in the event of its being wound up while he,
-  she or it is a member or within one year after he, she or it ceases
-  to be a member, for:
-  \begin{enumerate}
-  \item
-    payment of the charity's debts and liabilities incurred before he,
+  The liability of the members is limited to £1, being the amount that
+  each member undertakes to contribute to the assets of the association
+  in the event of its being wound up while he, she or it is a member or
+  within one year after he, she or it ceases to be a member, for:
+  \begin{enumerate}
+  \item
+    payment of the association's debts and liabilities incurred before he,
     she or it ceases to be a member;
@@
 \item
-  The charity's objects (``Objects'') are specifically restricted to
-  the following:
+  The objects of the association are:
   \begin{enumerate}
@@
 \item
-  The charity has power to do anything which is calculated to further
+  The association has power to do anything which is calculated to further
   its Objects or is conducive or incidental to doing so. In
-  particular, the charity has power:
-  \begin{enumerate}
-  \item
-    to raise funds. In doing so, the charity must not undertake any
-    taxable permanent trading activity and must comply with any
-    relevant statutory regulations;
+  particular, the association has power:
+  \begin{enumerate}
+  \item
+    to raise funds. 
   \item
@@
     to sell, lease or otherwise dispose of all or any part of the
-    property belonging to the charity. In exercising this power, the
-    charity must comply as appropriate with sections 36 and 37 of the
-    Charities Act 1993, as amended by the Charities Act 2006;
+    property belonging to the association.  
   \item
     to borrow money and to charge the whole or any part of the property
-    belonging to the charity as security for repayment of the money
+    belonging to the association as security for repayment of the money
     borrowed or as security for a grant or the discharge of an
-    obligation. The charity must comply as appropriate with sections 38
-    and 39 of the Charities Act 1993, as amended by the Charities Act
-    2006, if it wishes to mortgage land;
-  \item
-    to co-operate with other charities, voluntary bodies and statutory
-    authorities and to exchange information and advice with them;
-  \item
-    to establish or support any charitable trusts, associations or
-    institutions formed for any of the charitable purposes included in
-    the Objects;
+    obligation.
   \item
     to acquire, merge with or to enter into any partnership or joint
-    venture arrangement with any other charity;
+    venture arrangement with any other association;
   \item
@@
     to employ and remunerate such staff as are necessary for carrying
-    out the work of the charity. The charity may employ or remunerate a
+    out the work of the association. The association may employ or remunerate a
     director only to the extent it is permitted to do so by article \ref{cls:income-property}
@@
     \item
-      deposit or invest funds;
-    \item
-      employ a professional fund-manager; and
-    \item
-      arrange for the investments or other property of the charity to be
-      held in the name of a nominee; in the same manner and subject to
-      the same conditions as the trustees of a trust are permitted to do
-      by the Trustee Act 2000;
-    \end{enumerate}
-  \item
-    to provide indemnity insurance for the directors in accordance
-    with, and subject to the conditions in, section 73F of the
-    Charities Act 1993;
-  \item
-    to pay out of the funds of the charity the costs of forming and
-    registering the charity both as a company and as a charity;
+      deposit or invest funds; and
+    \item
+      employ a professional fund-manager.
+    \end{enumerate}
+  \item
+    to provide indemnity insurance for the directors.
+  \item
+    to pay out of the funds of the association the costs of forming and
+    registering the association;
   \end{enumerate}
@@
   \item
-    The income and property of the charity shall be applied solely
+    The income and property of the association shall be applied solely
     towards the promotion of the Objects.
@@
       A director is entitled to be reimbursed from the property of the
-      charity or may pay out of such property reasonable expenses
+      association or may pay out of such property reasonable expenses
       properly incurred by him or her when acting on behalf of the
-      charity.
-    \item
-      A director may benefit from trustee indemnity insurance cover
-      purchased at the charity's expense in accordance with, and subject
-      to the conditions in, section 73F of the Charities Act 1993.
-    \item
-      A director may receive an indemnity from the charity in the
+      association.
+    \item
+      A director may receive an indemnity from the association in the
       circumstances specified in article \ref{cls:directors-indemnity}.
@@
   \item
-    None of the income or property of the charity may be paid or
-    transferred directly or indirectly by way of dividend bonus or
-    otherwise by way of profit to any member of the charity. This does
-    not prevent a member who is not also a director receiving:
-    \begin{enumerate}
-    \item
-      a benefit from the charity in the capacity of a beneficiary of the
-      charity;
+    None of the income or property of the association may be paid or transferred,
+    directly or indirectly, by way of dividend, bonus, or otherwise by way of
+    profit to any member of the association. This does not prevent a member who
+    is not also a director receiving:
+    \begin{enumerate}
+    \item
+      a benefit from the association in the capacity of a beneficiary of the
+      association;
     \item
       reasonable and proper remuneration for any goods or services
-      supplied to the charity.
-    \end{enumerate}
-  \item
-    \label{scls:directors-remuneration} No director or connected person
-    may:
-    \begin{enumerate}
-    \item
-      buy any goods or services from the charity on terms preferential to
-      those applicable to members of the public;
-    \item
-      sell goods, services, or any interest in land to the charity;
-    \item
-      be employed by, or receive any remuneration from, the charity;
-    \item
-      receive any other financial benefit from the charity; unless:
-      \begin{enumerate}
-      \item
-        the payment is permitted by article \ref{scls:directors-scope}; or
-      \item
-        the directors obtain the prior written approval of the Commission
-        and fully comply with any procedures it prescribes. In this article
-        a `financial benefit' means a benefit, direct or indirect, which is
-        either money or has a monetary value.
-      \end{enumerate}
-    \end{enumerate}
-  \item
-    \label{scls:directors-scope}
-    \begin{enumerate}
-    \item
-      A director or connected person may receive a benefit from the
-      charity as a beneficiary provided it is available generally to the
-      beneficiaries of the charity.
-    \item
-      A director or connected person may enter into a contract for the
-      supply of services, or of goods that are supplied in connection
-      with the provision of services, to the charity where that is
-      permitted in accordance with, and subject to the conditions in
-      section 73A to 73C of the Charities Act 1993.
-    \item
-      Subject to article \ref{scls:supply-goods} a director or connected
-      person may provide the charity with goods that are not supplied in
-      connection with services provided to the charity by the director or
-      connected person. \label{art:directors-goods}
-    \item
-      A director or connected person may receive interest on money lent
-      to the charity at a reasonable and proper rate which must be 2\%
-      (or more) per annum below the base rate of a clearing bank to be
-      selected by the directors.
-    \item
-      A director or connected person may receive rent for premises let by
-      the director or connected person to the charity if the amount of
-      the rent and the other terms of the lease are reasonable and proper
-      and provided that the director concerned shall withdraw from any
-      meeting at which such a proposal or the rent or other terms of the
-      lease are under discussion.
-    \item
-      The directors may arrange for the purchase, out of the funds of the
-      charity, of insurance designed to indemnify the directors in
-      accordance with the terms of, and subject to the conditions in,
-      section 73F of the Charities Act 1993.
-    \end{enumerate}
-  \item \label{goods}
-    \label{scls:supply-goods} The charity and its directors may only
-    rely upon the authority provided by article
-    \ref{art:directors-goods} if each of the following conditions is
-    satisfied:
-    \begin{enumerate}
-    \item
-      The amount or maximum amount of the payment for the goods is set
-      out in an agreement in writing between:
-      \begin{enumerate}
-      \item
-        the charity or its directors (as the case may be); and
-      \item
-        the director or connected person supplying the goods
-        (``the supplier'') under which the supplier is to supply the goods
-        in question to or on behalf of the charity.
-      \end{enumerate}
-    \item
-      The amount or maximum amount of the payment for the goods does not
-      exceed what is reasonable in the circumstances for the supply of
-      the goods in question.
-    \item
-      The other directors are satisfied that it is in the best interests
-      of the charity to contract with the supplier rather than with
-      someone who is not a director or connected person. In reaching that
-      decision the directors must balance the advantage of contracting
-      with a director or connected person against the disadvantages of
-      doing so.
-    \item
-      The supplier is absent from the part of any meeting at which there
-      is discussion of the proposal to enter into a contract or
-      arrangement with him or her or it with regard to the supply of
-      goods to the charity.
-    \item
-      The supplier does not vote on any such matter and is not to be
-      counted when calculating whether a quorum of directors is present
-      at the meeting.
-    \item
-      The reason for their decision is recorded by the directors in the
-      minute book.
-    \item
-      A majority of the directors then in office are not in receipt of
-      remuneration or payments authorised by article
-      \ref{scls:directors-remuneration}.
-    \end{enumerate}
-  \item \label{def-charity}
-    In sub-clauses \ref{scls:director-reimburse} to \ref{goods}, ``charity'' shall include
-    any company in which the charity:
-    \begin{itemize}
-    \item
-      holds more than 50\% of the shares; or
-    \item
-      controls more than 50\% of the voting rights attached to the
-      shares; or
-    \item
-      has the right to appoint one or more directors to the board of the
-      company;
-    \end{itemize}
-  \item \label{def-connected}
-    In sub-clauses \ref{scls:directors-remuneration} to \ref{goods}, \ref{conflict-interest-loyalty},
-    and \ref{directors-validity-void} ``connected person'' means:
-    \begin{enumerate}
-    \item
-      \label{art:connected-child} a child, parent, grandchild,
-      grandparent, brother or sister of the director;
-    \item
-      \label{art:connected-spouse} the spouse or civil partner of the
-      director or of any person falling within paragraph (i) above;
-    \item
-      \label{art:connected-business} a person carrying on business in
-      partnership with the director or with any person falling within
-      paragraph (i) or (ii) above;
-    \item
-      an institution which is controlled –
-      \begin{enumerate}
-      \item
-        by the director or any connected person falling within paragraph (i) to (iii) above; or
-      \item
-        by two or more persons falling within sub-paragraph (A), when taken
-        together
-      \end{enumerate}
-    \item
-      a body corporate in which –
-      \begin{enumerate}
-        \item
-            the director or any connected person falling within paragraphs (i) to (iii) has a substantial interest; or
-        \item
-            two or more persons falling within sub-paragraph (A) who, when
-            taken together, have a substantial interest.
-      \end{enumerate}
-    \end{enumerate}
-  \item
-    For the purposes of interpreting the terms used in sub-clauses \ref{def-charity}
-    and \ref{def-connected}, paragraphs 2 to 4 of Schedule 5 to the Charities Act 1993
-    apply.
+      supplied to the association.
+    \end{enumerate}
   \end{enumerate}
@@
   \item
-    The subscribers to the memorandum are the first members of the
-    charity.
+    The subscribers to the memorandum are the first members of the association.
   \item
@@
     \item
-      apply to the charity in the form required by the directors; and
+      apply to the association in the form required by the directors; and
     \item
@@
       acting reasonably and properly, they consider it to be in the best
-      interests of the charity to refuse the application.
+      interests of the association to refuse the application.
     \item
@@
   \item
-    the member resigns by written notice to the charity unless, after
-    the resignation, there would be less than two members;
-  \item
-    any sum due from the member to the charity is not paid in full
+    the member resigns by written notice to the association unless, after
+    the resignation, there would be fewer than three members;
+  \item
+    any sum due from the member to the association is not paid in full
     within two weeks of it falling due;
@@
     the member is removed from membership by a resolution of the
-    directors that it is in the best interests of the charity that his
+    directors that it is in the best interests of the association that his
     or her or its membership is terminated. A resolution to remove a
@@
       the member or, at the option of the member, the member's
-      representative (who need not be a member of the charity) has been
+      representative (who need not be a member of the association) has been
       allowed to make representations to the meeting.
@@
     The minimum periods of notice required to hold a general meeting of
-    the charity are:
+    the association are:
     \begin{enumerate}
@@
   person who was entitled to receive notice of the meeting did not
-  receive it because of an accidental omission by the charity.
+  receive it because of an accidental omission by the association.
 
@@
       The result of the vote must be recorded in the minutes of the
-      charity but the number or proportion of votes cast need not be
+      association but the number or proportion of votes cast need not be
       recorded.
@@
     \item
-      is delivered to the charity in accordance with the articles and any
+      is delivered to the association in accordance with the articles and any
       instructions contained in the notice of the general meeting to
@@
   \item
-    The charity may require proxy notices to be delivered in a
+    The association may require proxy notices to be delivered in a
     particular form, and may specify different forms for different
@@
         of it, even though a valid proxy notice has been delivered to the
-        charity by or on behalf of that person.
+        association by or on behalf of that person.
         \item
         An appointment under a
-        proxy notice may be revoked by delivering to the charity a notice
+        proxy notice may be revoked by delivering to the association a notice
         in writing given by or on behalf of the person by whom or on whose
@@
   \item
-    Any organisation that is a member of the charity may nominate any
-    person to act as its representative at any meeting of the charity.
-  \item
-    The organisation must give written notice to the charity of the
+    Any organisation that is a member of the association may nominate any
+    person to act as its representative at any meeting of the association.
+  \item
+    The organisation must give written notice to the association of the
     name of its representative. The representative shall not be
     entitled to represent the organisation at any meeting unless the
-    notice has been received by the charity. The representative may
+    notice has been received by the association. The representative may
     continue to represent the organisation until written notice to the
-    contrary is received by the charity.
-  \item
-    Any notice given to the charity will be conclusive evidence that
+    contrary is received by the association.
+  \item
+    Any notice given to the association will be conclusive evidence that
     the representative is entitled to represent the organisation or
-    that his or her authority has been revoked. The charity shall not
+    that his or her authority has been revoked. The association shall not
     be required to consider whether the representative has been
@@
   \begin{enumerate}
+  \item
     A director must be a natural person aged 16 years or older.
-  \item
     No one may be appointed a director if he or she would be
-    disqualified from acting under the provisions of article \ref{director-cease}.
-  \end{enumerate}
+    disqualified from acting under the provisions of article
+    \ref{director-cease}.
   \item
@@
     The first directors shall be those persons notified to Companies
-  House as the first directors of the charity.
+    House as the first directors of the association.
 
@@
     on his or her behalf at meetings of the directors.
+  \end{enumerate}
 
@@
   \item
-    The directors shall manage the business of the charity and may
-    exercise all the powers of the charity unless they are subject to
+    The directors shall manage the business of the association and may
+    exercise all the powers of the association unless they are subject to
     any restrictions imposed by the Companies Acts, the articles or any
@@
 \item
-  The charity may by ordinary resolution:
+  The association may by ordinary resolution:
   \begin{enumerate}
@@
     not less than fourteen nor more than thirty-five clear days before
-    the date of the meeting, the charity is given a notice that:
+    the date of the meeting, the association is given a notice that:
     \begin{enumerate}
@@
       contains the details that, if the person were to be appointed, the
-      charity would have to file at Companies House; and
+      association would have to file at Companies House; and
     \item
@@
 \item
-  The appointment of a director, whether by the charity in general
+  The appointment of a director, whether by the association in general
   meeting or by the other directors, must not cause the number of
@@
     \item
-    is disqualified from acting as a trustee by virtue of section 72 of
-    the Charities Act 1993 (or any statutory re-enactment or
-    modification of that provision);
-    \item
-    ceases to be a member of the charity; 
+    ceases to be a member of the association; 
     \item
@@
     \item 
-    resigns as a director by notice to the charity (but only if at
+    resigns as a director by notice to the association (but only if at
     least two directors will remain in office when the notice of
@@
     \item
-      no expenditure may be incurred on behalf of the charity except in
+      no expenditure may be incurred on behalf of the association except in
       accordance with a budget previously agreed with the directors.
@@
   direct or indirect, which he or she has in a proposed transaction
-  or arrangement with the charity or in any transaction or
-  arrangement entered into by the charity which has not previously
+  or arrangement with the association or in any transaction or
+  arrangement entered into by the association which has not previously
   been declared. A director must absent himself or herself from any
@@
   conflict will arise between his or her duty to act solely in the
-      interests of the charity and any personal interest (including but
+      interests of the association and any personal interest (including but
   not limited to any personal financial interest).
@@
       the unconflicted directors consider it is in the interests of the
-      charity to authorise the conflict of interests in the circumstances
+      association to authorise the conflict of interests in the circumstances
       applying.
@@
     such a conflict which does not involve a direct or indirect benefit
-    of any nature to a director or to a connected person.
+    of any nature to a director.
   \end{enumerate}
@@
   \item \label{directors-validity-void}
-    Article \ref{directors-validity} does not permit a director or a connected person to
+    Article \ref{directors-validity} does not permit a director to
     keep any benefit that may be conferred upon him or her by a
@@
         \item
-            proceedings at meetings of the charity;
+            proceedings at meetings of the association;
         \item
@@
 
-\section{Annual Report and Register of Charities}
-
-\item
-  \begin{enumerate}
-  \item
-    The directors must comply with the requirements of the Charities
-    Act 1993 with regard to the:
-    \begin{enumerate}
-    \item
-      transmission of a copy of the statements of account to the
-      Commission;
-    \item
-      preparation of an Annual Report and the transmission of a copy of
-      it to the Commission;
-    \item
-      preparation of an Annual Return and its transmission to the
-      Commission.
-    \end{enumerate}
-  \item
-    The directors must notify the Commission promptly of any changes to
-    the charity's entry on the Central Register of Charities.
-  \end{enumerate}
-
 \section{Means of Communication to be Used}
@@
     Subject to the articles, anything sent or supplied by or to the
-    charity under the articles may be sent or supplied in any way in
+    association under the articles may be sent or supplied in any way in
     which the Companies Act 2006 provides for documents or information
     which are authorised or required by any provision of that Act to be
-    sent or supplied by or to the charity.
+    sent or supplied by or to the association.
   \item
@@
   \item
-    The charity may give any notice to a member either:
+    The association may give any notice to a member either:
     \begin{enumerate}
@@
   \item
-    A member who does not register an address with the charity or who
+    A member who does not register an address with the association or who
     registers only a postal address that is not within the United
     Kingdom shall not be entitled to receive any notice from the
-    charity.
-  \end{enumerate}
-\item
-  A member present in person at any meeting of the charity shall be
+    association.
+  \end{enumerate}
+\item
+  A member present in person at any meeting of the association shall be
   deemed to have received notice of the meeting and of the purposes
@@
     conclusive where the company can demonstrate that it was
-    accepted by an electronic mail host for that address
+    accepted by an electronic mail host for that address.
   \item
@@
   \item
-    The charity shall indemnify any director against any
+    The association may indemnify any director against any
     liability incurred by him or her or it in that capacity, to the
@@
     In this article a ``relevant director'' means any director or
-    former director of the charity.
+    former director of the association.
   \end{enumerate}
@@
     rules or bye laws as they may deem necessary or expedient for the
-    proper conduct and management of the charity.
+    proper conduct and management of the association.
   \item
@@
     \item
-      the admission of members of the charity (including the admission of
+      the admission of members of the association (including the admission of
       organisations to membership) and the rights and privileges of such
@@
     \item
-      the conduct of members of the charity in relation to one another,
-      and to the charity's employees and volunteers;
+      the conduct of members of the association in relation to one another,
+      and to the association's employees and volunteers;
     \item
       the setting aside of the whole or any part or parts of the
-      charity's premises at any particular time or times or for any
+      association's premises at any particular time or times or for any
       particular purpose or purposes;
@@
   \item
-    The charity in general meeting has the power to alter, add to or
+    The association in general meeting has the power to alter, add to or
     repeal the rules or bye laws.
@@
     bring the rules and bye laws to the notice of members of the
-    charity.
+    association.
   \item
     The rules or bye laws shall be binding on all members of the
-    charity. No rule or bye law shall be inconsistent with, or shall
+    association. No rule or bye law shall be inconsistent with, or shall
     affect or repeal anything contained in, the articles.
@@
   \item \label{dissolve-transfer}
-    The members of the charity may at any time before, and in
+    The members of the association may at any time before, and in
     expectation of, its dissolution resolve that any net assets of the
-    charity after all its debts and liabilities have been paid, or
+    association after all its debts and liabilities have been paid, or
     provision has been made for them, shall on or before the
-    dissolution of the charity be applied or transferred in any of the
+    dissolution of the association be applied or transferred in any of the
     following ways:
@@
     \item
-      by transfer to any charity or charities for purposes similar to the
+      by transfer to any association for purposes similar to the
       Objects; or
     \item
-      to any charity or charities for use for particular purposes that
+      to any association for use for particular purposes that
       fall within the Objects.
@@
   \item
-    Subject to any such resolution of the members of the charity, the
-    directors of the charity may at any time before and in expectation
-    of its dissolution resolve that any net assets of the charity after
+    Subject to any such resolution of the members of the association, the
+    directors of the association may at any time before and in expectation
+    of its dissolution resolve that any net assets of the association after
     all its debts and liabilities have been paid, or provision made for
-    them, shall on or before dissolution of the charity be applied or
+    them, shall on or before dissolution of the association be applied or
     transferred:
@@
   \item
-    In no circumstances shall the net assets of the charity be paid to
-    or distributed among the members of the charity (except to a member
-    that is itself a charity) and if no resolution in accordance with
+    In no circumstances shall the net assets of the association be paid to
+    or distributed among the members of the association (except to a member
+    that is itself a association) and if no resolution in accordance with
     article \ref{dissolve-transfer} is passed by the members or the directors the net
-    assets of the charity shall be applied for charitable purposes as
+    assets of the association shall be applied for charitable purposes as
     directed by the Court or the Commission.
   \end{enumerate}
-\end{enumerate}

### 2012-12-17 annualreports/2011/balancesheet.tex
Fixed 2011 annual report

@@
 Prepaid Subscriptions                           & -610   &       &       &      \\
-{\bf Net current assets}                        &        & 20,908 &       & 7,285 \\
+{\bf Net current assets}                        &        & 12,263 &       & 7,299 \\
 \cmidrule(r){2-3} \cmidrule(r){4-5} \\
@@
 {\bf Capital and Reserves}&\\
-Income and expenditure account                  &        & 10,267 &       & 8,339 \\
+Income and expenditure account                  &        & 17,787 &       & 8,339 \\
 \bottomrule
@@
 
-Approved by the Board for issue on the 28\superscript{th} of December 2011
+Approved by the Board for issue on the 22\superscript{nd} of January 2012
 \vspace{48pt}

### 2012-12-17 annualreports/2012/balancesheet.tex
2012 annual report

--- 2012-12-17 annualreports/2011/balancesheet.tex
@@
 \section{Balance Sheet}
-31\superscript{st} March 2011
+31\superscript{st} March 2012
 
@@
 \toprule
-                            & \multicolumn{2}{c}{2011} &  \multicolumn{2}{c}{2010} \\
+                            & \multicolumn{2}{c}{2012} &  \multicolumn{2}{c}{2011} \\
 \cmidrule(r){2-3} \cmidrule(r){4-5}
@@
 {\bf Fixed Assets}                             &          &         &        &        \\
-{\bf Tangible fixed assets}                     &        & 5,525 &       & 1,040 \\
+{\bf Tangible fixed assets}                    &          & 5,149   &        & 5,525  \\
 \cmidrule(r){2-3} \cmidrule(r){4-5} \\
 {\bf Current Assets}                           &          &         &        &        \\
-Rental Deposit                                  & 7,696  &       &       &       \\
-Cash at bank and in hand                        & 7,688  &       & 8,642 &       \\
-Creditors: amounts falling due within one year  & -2,511 &       & -1,343&      \\
-Prepaid Subscriptions                           & -610   &       &       &      \\
-{\bf Net current assets}                        &        & 12,263 &       & 7,299 \\
+Rental Deposit                                 & 7,696    &         & 7,696  &        \\
+Inventory                                      & 163      &         & 0      &        \\
+Cash at bank and in hand                       & 14,889   &         & 7,688  &        \\
+Creditors: amounts falling due within one year & -167     &         & -2,511 &       \\
+Prepaid Subscriptions                          & 0        &         & -610   &       \\
+{\bf Net current assets}                       &          & 27,898  &        & 12,263 \\
 \cmidrule(r){2-3} \cmidrule(r){4-5} \\
-{\bf Total assets less current liabilities}     &        & 17,787 &       & 8,339 \\
+{\bf Total assets less current liabilities}    &          & 27,732  &        & 17,787 \\
 \cmidrule(r){2-3} \cmidrule(r){4-5}  \\
 {\bf Capital and Reserves}&\\
-Income and expenditure account                  &        & 17,787 &       & 8,339 \\
+Income and expenditure account                 &          & 27,732  &        & 17,787 \\
 \bottomrule
@@
 
-Approved by the Board for issue on the 22\superscript{nd} of January 2012
+Approved by the Board for issue on TBC
 \vspace{48pt}

### 2012-12-17 annualreports/2012/directorsreport.tex
2012 annual report

--- 2011-05-15 annualreports/2011/directorsreport.tex
@@
 
-\subsection{Objects of the Company}
+\subsection{Objects of the Association}
 
-The stated Objects of the Hackspace Foundation are:
+The stated Objects of London Hackspace are:
 
 \begin{itemize}
-    \item To promote and support science, engineering, and art.
+    \item to promote and encourage technical, scientific, and artistic skills through social collaboration and education; and
+    \item to provide and maintain shared community workspace and equipment in Greater London.
 \end{itemize}
@@
 
-The Hackspace Foundation is a Company Limited by Guarantee operating as a membership association.
-The company has a Board of up to eight Directors who are elected by the membership and serve for a three-year term,
-although this is mainly a symbolic role with most decisions made by membership consensus.
+The London Hackspace is a Company Limited by Guarantee operating as a membership association.
+The company has a Board of up to nine Directors (known commonly as "Trustees") who are elected yearly by the membership and serve for a three-year term.
+The role of the Trustees is primarily to provide overall guidance; day-to-day management of the facilities is handled by members on a volunteer basis.
 
-As the Foundation has grown since its formation in February 2009, it has historically not been possible
-to reliably determine if it is eligible for charitable status. Combined with the administrative overhead of doing so,
-this has so far prevented the Hackspace Foundation from becoming a registered charity.
+\subsection{Charitable Status}
 
-Since the company is becoming more mature, it is becoming more clear that it is likely to be eligible for charitable status,
-and we anticipate looking into applying within the next year.
+In our previous Annual Report, we raised the possibility of applying for charitable status.
+After discussion with the Charity Commission during 2011, we concluded that this would not be
+an appropriate route for London Hackspace to go down at this time.
 
@@
 
-At the beginning of the 2010/2011 year, the London Hackspace was based in an 800 sq ft, unheated space in Barnsbury.
-In July 2010 we moved to a 1300 sq ft space in Cremer Street, E2, and on January 1\(^{st}\) 2011 the space was expanded into
-the adjacent unit to increase our space to 2600 sq ft.
-
-Currently our space comprises desk space across two separate rooms, sofas, a kitchen, and a sizeable workshop with woodworking,
-metalworking and other fabrication facilities.
-
-Recent equipment purchases include a laser cutter for cutting and etching wood and plastic, and large lathe/mill for metalworking.
-All this equipment is available for members to use for free or with a small contribution to equipment running costs.
+TBC
 
@@
 
-The Hackspace Foundation is a membership association, and membership is open to everyone.
-Members receive 24-hour access to the space, storage space, and voting rights in return for a membership subscription.
-
-The minimum membership subscription is £5 per month, and members are encouraged to pay what they consider their
-membership to be worth.
-
-Membership subscriptions are the primary source of income for the Hackspace Foundation, and in 2010/11 our
-membership rapidly grew by 600\% from 41 to 252 people.
-
-\subsection{Services for Non-Members}
-
-Although we encourage anyone who finds the London Hackspace useful to become a member, we don't limit our services to members.
-Non-members can use our facilities under the supervision of a member, and we run events (both free and paid) which are open to non-members.
-
-There are many individual events organised by members on a regular basis, which are usually free and open to the public. Regular events include:
-
-\begin{itemize}
-    \item Weekly Meetups - our weekly public social events.
-    \item DIY Bio - workshops and lectures on biology.
-    \item Young Hackspace - free events for children aged between 6 and 10.
-\end{itemize}
-
-We also allow other like-minded non-profit groups to hire out sections of our space at cost - generally much cheaper than other similar venues.
-
-\subsection{Public Benefit}
-
-The London Hackspace is not currently a registered charity (see the Organisational Structure section on page \pageref{ref_structure} for more details),
-which would require it to publish details of the public benefit it delivers. Nonetheless, the Directors feel it is appropriate to do so.
-
-We believe the London Hackspace delivers charitable benefits under two of the headings allowed by the Charities Act 2006:
-firstly and primarily through the advancement of the arts, culture, heritage or science, and secondly through the advancement of education.
-
-As entry to the London Hackspace is free of charge for non-members, and the minimum membership is a modest fee, we
-believe there are no unreasonable restrictions on access to the benefits which are therefore available to the public in accordance with the
-definition of the Act.
+TBC
 
@@
 
-The Hackspace Foundation aims to keep three months worth of monthly running costs as a reserve. This currently amounts to £12,486.
-
-Due to the significant membership growth of the London Hackspace during 2010/11, it was decided to spend some of the reserve on expanding the space.
-The majority of this was spent on lease deposits. At the end of the financial year, our balance was £7,568.
+London Hackspace aims to keep three months worth of monthly running costs as a reserve.
 
@@
 
-Approved by the Board for issue on <date>
+Approved by the Board for issue on TBC
 \vspace{48pt}

### 2012-12-27 annualreports/2012/balancesheet.tex
More 2012 report updates

@@
 Rental Deposit                                 & 7,696    &         & 7,696  &        \\
-Inventory                                      & 163      &         & 0      &        \\
+Inventory                                      & 463      &         & 0      &        \\
 Cash at bank and in hand                       & 14,889   &         & 7,688  &        \\
@@
 Prepaid Subscriptions                          & 0        &         & -610   &       \\
-{\bf Net current assets}                       &          & 27,898  &        & 12,263 \\
+{\bf Net current assets}                       &          & 22,881  &        & 12,263 \\
 \cmidrule(r){2-3} \cmidrule(r){4-5} \\
-{\bf Total assets less current liabilities}    &          & 27,732  &        & 17,787 \\
+{\bf Total assets less current liabilities}    &          & 28,030  &        & 17,787 \\
 \cmidrule(r){2-3} \cmidrule(r){4-5}  \\
 {\bf Capital and Reserves}&\\
-Income and expenditure account                 &          & 27,732  &        & 17,787 \\
+Income and expenditure account                 &          & 28,030  &        & 17,787 \\
 \bottomrule
@@
 
-Approved by the Board for issue on TBC
+Approved by the Board for issue on the 27\superscript{th} December 2012.
 \vspace{48pt}

### 2013-01-25 annualreports/2012/balancesheet.tex
Fix date

@@
 
-{\footnotesize For the financial period ended 31 March 2011 the
+{\footnotesize For the financial period ended 31 March 2012 the
 company was entitled to exemption from audit under section 477 of the
@@
 
-Approved by the Board for issue on the 27\superscript{th} December 2012.
+Approved by the Board for issue on the 14\superscript{th} January 2013.
 \vspace{48pt}

### 2014-09-13 constitution/articles-body.tex
Add missing tag
Increase maximum size of the board to 9
Initial provision for electronic elections

@@
   \item
-    The number of directors shall be not less than three, nor more than eight.
+    The number of directors shall be not less than three, nor more than nine.
 
@@
 
+\section{Directors Elections}
+\item
+  \begin{enumerate}
+    \item Directors elections must be called by the Board
+      \begin{enumerate}
+        \item in the case of the first election: before the end of the calendar year following
+                the year in which the association was created.
+        \item in the case of subsequent elections: before the end of the calendar year following
+                the year in which the last election was held.
+      \end{enumerate}
+    \item
+      The directors election must be carried out by electronically polling the membership as follows:
+      \begin{enumerate}
+        \item The Meek STV voting method with a "no further places" candidate must be used.
+        \item All members of the association at the time the election commences are eligible to vote.
+        \item The voting period of the election must be no less than 14 days and no more than 28 days.
+        \item The quorum of the election must be at least 10\% of eligible voters.
+      \end{enumerate}
+    \item Directors standing for re-election will remain directors until the successful conclusion
+          of the election.
+    \item Notice of the election must be given at the time the election starts to all members eligible
+          to vote who have registered an electronic mail address with the association.
+   \end{enumerate}
+
 \section{Retirement of Directors}
-
-\item
-    At the first annual general meeting all the directors must retire from
-    office unless by the close of the meeting the members have failed to
-    elect sufficient directors to hold a quorate meeting of the directors. At
-    each subsequent annual general meeting one-third of the directors or, if
-    their number is not three or a multiple of three, the number nearest to
-    one-third, must retire from office. If there is only one director he or she
-    must retire.
+\item
+    \begin{enumerate}
+        \item At the first directors election, all the directors must retire from office unless the election
+              fails to elect sufficient directors to hold a quorate meeting of the directors.
+        \item At each subsequent directors election, one-third of the directors or, if their number is
+              not three or a multiple of three, the number nearest to one-third, must retire from office.
+              If there is only one director, they must retire.
+        \item The directors to retire by rotation shall be those who have been longest in office since their
+              last appointment. If any directors became or were appointed directors
+              on the same day, those to retire shall (unless they otherwise agree among themselves)
+              be determined by lot.
+        \item Retiring directors may stand for re-election.
+    \end{enumerate}
 
@@
     assets of the association shall be applied for charitable purposes as
-    directed by the Court or the Commission.
-  \end{enumerate}
+    directed by the Court.
+  \end{enumerate}
+\end{enumerate}

### 2014-09-13 constitution/articles-body.tex
Remove article 32 as it duplicates 24(b)
Remove article 7 (classes of membership)
We have no intention of using it, and if we do anything that drastic it
should require a special resolution anyway.

@@
 
-\section{Classes of Membership}
-
-\item
-  \label{cls:members}
-  \begin{enumerate}
-  \item
-    The directors may establish classes of membership with different
-    rights and obligations and shall record the rights and obligations
-    in the register of members.
-  \item
-    The directors may not directly or indirectly alter the rights or
-    obligations attached to a class of membership.
-  \item
-    The rights attached to a class of membership may only be varied if:
-    \begin{enumerate}
-    \item
-      three-quarters of the members of that class consent in writing to
-      the variation; or
-    \item
-      a special resolution is passed at a separate general meeting of the
-      members of that class agreeing to the variation.
-    \end{enumerate}
-  \item
-    The provisions in the articles about general meetings shall apply
-    to any meeting relating to the variation of the rights of any class
-    of members.
-  \end{enumerate}
-
 \section{Termination of Membership}
@@
 \item
-  Subject to article \ref{cls:members}, every member, whether an individual or an
-  organisation, shall have one vote.
+  Every member, whether an individual or an organisation, shall have one vote.
 
@@
   \end{enumerate}
-\item
-  The appointment of a director, whether by the association in general
-  meeting or by the other directors, must not cause the number of
-  directors to exceed any number fixed as the maximum number of
-  directors.
 

### 2014-11-16 constitution/articles-body.tex
Correct duplicated clause 38.c.iii
Corrected form is from earlier drafts of the articles.
Make clear that membership requires a valid email address
Fix election/re-election confusion
Remove duplicate directors retirement clause

@@
     \item
-      apply to the association in the form required by the directors; and
-    \item
-      are approved by the directors.
+      apply to the association in the form required by the directors;
+    \item
+      supply a valid e-mail address; and
+    \item
+      are approved by the directors
     \end{enumerate}
@@
 
-\item
-  \begin{enumerate}
-  \item
-    The directors to retire by rotation shall be those who have been
-    longest in office since their last appointment. If any directors
-    became or were appointed directors on the same day those to retire
-    shall (unless they otherwise agree among themselves) be determined
-    by lot.
-  \item
-    If a director is required to retire at an annual general meeting by
-    a provision of the articles the retirement shall take effect upon
-    the conclusion of the meeting.
-  \end{enumerate}
-
 \section{Appointment of Directors}
@@
   \item
-    he or she is recommended for re-election by the directors; or
+    he or she is recommended for election by the directors; or
   \item
@@
                 \item
-                    the identities of the directors involved; and
+                    the substance of the discussion.
             \end{enumerate}

### 2014-12-10 constitution/articles-body.tex
Fix heading position (thanks Oxford!)
Clarify retirement of existing directors

@@
   \end{enumerate}
+
+\section{Votes of Members}
+
 \item
   Every member, whether an individual or an organisation, shall have one vote.
-
-\section{Votes of Members}
 
@@
       \end{enumerate}
-    \item Directors standing for re-election will remain directors until the successful conclusion
+    \item A director standing for re-election will remain a director until the successful conclusion
           of the election.
+    \item A director retiring and not standing for re-election will cease to be a director at the
+          start of the election.
     \item Notice of the election must be given at the time the election starts to all members eligible

### 2015-02-13 constitution/articles-body.tex
Remove the requirement to have a meeting to remove a member

@@
     directors that it is in the best interests of the association that his
-    or her or its membership is terminated. A resolution to remove a
-    member from membership may only be passed if:
-    \begin{enumerate}
-    \item
-      the member has been given at least twenty-one days' notice in
-      writing of the meeting of the directors at which the resolution
-      will be proposed and the reasons why it is to be proposed;
-    \item
-      the member or, at the option of the member, the member's
-      representative (who need not be a member of the association) has been
-      allowed to make representations to the meeting.
-    \end{enumerate}
+    or her or its membership is terminated.
 \end{enumerate}

### 2015-12-01 constitution/articles-body.tex
Remove "No Further Places" wording for elections
Fixes #4
Remove reference to annual general meeting
Fixes #3

--- 2014-12-10 constitution/articles-body.tex
@@
       \begin{enumerate}
-        \item The Meek STV voting method with a "no further places" candidate must be used.
+        \item The Meek STV voting method must be used.
         \item All members of the association at the time the election commences are eligible to vote.
@@
     A director appointed by a resolution of the other directors must
-    retire at the next annual general meeting and must not be taken
-    into account in determining the directors who are to retire by
-    rotation.
+    retire at the next directors election  and must not be taken into
+    account in determining the directors who are to retire by rotation.
   \end{enumerate}

### 2015-12-01 constitution/articles-body.tex
Remove hearing requirement for removal of membership
Fixes #2

@@
     directors that it is in the best interests of the association that his
-    or her or its membership is terminated. A resolution to remove a
-    member from membership may only be passed if:
-    \begin{enumerate}
-    \item
-      the member has been given at least twenty-one days' notice in
-      writing of the meeting of the directors at which the resolution
-      will be proposed and the reasons why it is to be proposed;
-    \item
-      the member or, at the option of the member, the member's
-      representative (who need not be a member of the association) has been
-      allowed to make representations to the meeting.
-    \end{enumerate}
+    or her or its membership is terminated. Such a resolution may only be
+    passed after the Board has exhausted all other options under the
+    Grievance Procedure.
 \end{enumerate}

### 2015-12-10 constitution/articles-body.tex
Clarify that a special resolution is required to remove a member.
Fixes #6

@@
     passed after the Board has exhausted all other options under the
-    Grievance Procedure.
+    Grievance Procedure;
+   \item
+    a special resolution is passed stating that it is in the best interests
+    of the association that his/her membership is terminated. Such a
+    resolution may only be passed if the member has been given 14 days'
+    notice of the resolution, and has been allowed to provide a statement
+    to the general meeting.
    \end{enumerate}

### 2017-11-14 constitution/articles-body.tex
Clarify that a member must be banned before being removed
Update articles for 2017 EGM changes

--- 2015-12-01 constitution/articles-body.tex
@@
     out the work of the association. The association may employ or remunerate a
-    director only to the extent it is permitted to do so by article \ref{cls:income-property}
-    and provided it complies with the conditions in that article;
+    director only to the extent it is permitted to do so by
+    article~\ref{cls:income-property} and provided it complies with the conditions
+    in that article;
   \item
@@
   \item
-    Membership is open to other individuals or organisations who:
+    Membership is open to other individuals who:
     \begin{enumerate}
@@
   \item
-    the member dies or, if it is an organisation, ceases to exist;
+    the member dies;
   \item
@@
     or her or its membership is terminated. Such a resolution may only be
-    passed after the Board has exhausted all other options under the
-    Grievance Procedure.
+    passed after the Board has banned the member under the Grievance Procedure;
+  \item
+    A special resolution is passed stating that it is in the best interests of
+    the association that his/her membership is terminated. Such a resolution may
+    only be passed if the member has been given 14 days' notice of the resolution,
+    and has been allowed to provide a statement to the general meeting.'
 \end{enumerate}
@@
       the business to be conducted at the meeting.
-  \item
-    The authorised representative of a member organisation shall be
-    counted in the quorum.
   \end{enumerate}
@@
   person who is chairing the meeting shall be final.
-\item
-  \begin{enumerate}
-  \item
-    Any organisation that is a member of the association may nominate any
-    person to act as its representative at any meeting of the association.
-  \item
-    The organisation must give written notice to the association of the
-    name of its representative. The representative shall not be
-    entitled to represent the organisation at any meeting unless the
-    notice has been received by the association. The representative may
-    continue to represent the organisation until written notice to the
-    contrary is received by the association.
-  \item
-    Any notice given to the association will be conclusive evidence that
-    the representative is entitled to represent the organisation or
-    that his or her authority has been revoked. The association shall not
-    be required to consider whether the representative has been
-    properly appointed by the organisation.
-  \end{enumerate}
 
@@
           to vote who have registered an electronic mail address with the association.
+    \item The number of directors to be elected will be decided by the Board, subject to Article 23(b),
+          but must not be less than two. This number should be included in the notice of election.
    \end{enumerate}
@@
     A director appointed by a resolution of the other directors must
-    retire at the next directors election  and must not be taken into
-    account in determining the directors who are to retire by rotation.
+    retire at the next directors election and must not be taken
+    into account in determining the directors who are to retire by
+    rotation.
   \end{enumerate}
@@
     \item
-      the admission of members of the association (including the admission of
-      organisations to membership) and the rights and privileges of such
-      members, and the entrance fees, subscriptions and other fees or
-      payments to be made by members;
+      the admission of members of the association and the rights and
+      privileges of such members, and the entrance fees, subscriptions
+      and other fees or payments to be made by members;
     \item
